---
title: "Establishing relationships between cwc and MPa, Part 2"
author: "Indra Boving"
date: "11/9022"
output:
  html_document: default
  word_document: default
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(tidyverse)
library(boot)
source(here::here("scripts", "scripts_functions", "figure_info.R"))

library(data.table)
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(readxl)
library(gridExtra)
#library(calecopal)
library(rstatix)
library(vars)
library(MuMIn)
library(lme4) #for mixed effects models
library(arm)
library(nlme)
select = dplyr::select

library(cowplot)
library(grid)
library(gridExtra)

#source(here::here("scripts", "scripts_functions", "figure_info.R"))

datver <- "20230724" #make sure this matches the datver in the processing script
dataversion <- paste0("Data_", datver)
```

#DATA

```{r}
#CWC data: 
data_og_cwc <- read_csv(here("processed-data", paste0("cwc_analysis",datver,".csv")), show_col_types = F) %>%  
  filter(species %in% c("blue oak")) %>% 
  select(tree, week, water_potential, cwc, time_season, time, site, date_wp, date_shift) %>% 
  mutate(water_potential = -1*water_potential) %>% 
  distinct() %>% 
  #filter(cwc > 0) %>% #to try running with CWC = 0.
   # filter(!tree %in% c(2012, 2011)) %>% 
  filter(!(tree %in% c(2346))) %>% #this tree seems to have a problem with post-leafout cwc - all 0s - likely becuase the canopy was too small to see. 
  filter(!week %in% c(11, 9, 18)) #week 11 only has 9 midday measurements and acts really odd (2022-03-15), 9 just had 3 measurements 

data_og_cwc%>% 
  filter(time == "md") %>% 
  group_by(week, date_shift) %>% 
  summarise(n = n())

##LMA, LWA, LWC data: 
data_qudo_lma <- read_csv(here("processed-data", paste0("wp_wc_rwc_",datver,".csv"))) %>% 
 # filter(time %in% c("md")) %>% 
  group_by(tree, week) %>% 
  mutate(lma_g_cm2 = mean(lma_g_cm2, na.rm = T), 
         water_potential = -1*water_potential) %>% 
  filter(species %in% c("blue oak")) %>% 
  select(week, time, tree, species, lma_g_cm2, water_potential, lwc_mean, lwa_g_cm2) %>% 
  distinct()
```

```{r}
df <- merge(data_qudo_lma, data_og_cwc %>% select(-water_potential),
            , by = c("tree", "week", "time"), all = T) 
```


```{r}
df %>% ggplot(aes(y = water_potential, x = lwc_mean, color = time)) +
geom_point()
  # pivot_longer(names_to = "var", 
  #              values_to = "value", 
  #              cols = c("water_potential", "lwc_mean", "lwa_g_cm2", "lma_g_cm2")) %>% 
  # ggplot(aes(y = value, 
  #            ))


```


#--------------

#Mixed effects models: Table S1
```{r}
library(lme4)
library(broom.mixed)  # For tidy output of mixed models
library(dplyr)
# Filter the data to exclude rows with missing values in the variables of interest
df_filtered <- df %>% 
  filter(!is.na(cwc) & !is.na(lma_g_cm2) & !is.na(water_potential))


# Fit models with different combinations of predictors
model_cwc <- lmer(water_potential ~ cwc + (1 | tree), data = df_filtered)
model_lma <- lmer(water_potential ~ lma_g_cm2 + (1 | tree), data = df_filtered)
model_time_season <- lmer(water_potential ~ time_season + (1 | tree), data = df_filtered)
model_lwa <- lmer(water_potential ~ lwa_g_cm2 + (1 | tree), data = df_filtered)
model_lwc <- lmer(water_potential ~ lwc_mean + (1 | tree), data = df_filtered)
model_combined <- lmer(water_potential ~ cwc + lma_g_cm2 + time_season + (1 | tree), data = df_filtered)

# New models with additional combinations
model_lwc_time <- lmer(water_potential ~ lwc_mean + time_season + (1 | tree), data = df_filtered)
model_lwa_time <- lmer(water_potential ~ lwa_g_cm2 + time_season + (1 | tree), data = df_filtered)
model_lwc_lma_time <- lmer(water_potential ~ lwc_mean + lma_g_cm2 + time_season + (1 | tree), data = df_filtered)
model_lwa_lma_time <- lmer(water_potential ~ lwa_g_cm2 + lma_g_cm2 + time_season + (1 | tree), data = df_filtered)

# List of models
models <- list(
  cwc = model_cwc,
  lma = model_lma,
  time_season = model_time_season,
  lwa = model_lwa,
  lwc = model_lwc,
  combined = model_combined,
  lwc_time = model_lwc_time,
  lwa_time = model_lwa_time,
  lwc_lma_time = model_lwc_lma_time,
  lwa_lma_time = model_lwa_lma_time
)

# Create a summary table of delta AIC for each model
model_summary <- bind_rows(
  lapply(names(models), function(model_name) {
    model <- models[[model_name]]
    model_aic <- AIC(model)
    
    # Collect model structure (excluding random effect part) and delta AIC (AIC - min AIC)
    model_formula <- deparse(formula(model))
    model_formula <- gsub("\\s*\\+\\s*\\(1\\s*\\|\\s*tree\\)", "", model_formula)  # Remove random effect part
    
    data.frame(
      model = model_formula,
      delta_AIC = model_aic - min(sapply(models, AIC))
    )
  })
)

# Arrange and print table by delta AIC
model_summary <- model_summary %>% arrange(delta_AIC) %>%
  mutate(
    delta_AIC = round(delta_AIC, 3)
  )
print(model_summary)

write_csv(model_summary, here("processed-data", "model results", "qudo_mems.csv"))
```


What random intercept structure is better?

```{r}
# Load necessary library
library(lme4)

# Fit the random intercept model
model_intercept <- lmer(water_potential ~ cwc + time_season + (1 | tree), data = df_filtered, REML = TRUE)

# Fit the random slope model, allowing slopes for `cwc` to vary by tree
model_slope <- lmer(water_potential ~ cwc + time_season + (1 + cwc | tree), data = df_filtered, REML = TRUE)

# Compare the models using AIC, BIC, and likelihood ratio test
summary(model_intercept)
summary(model_slope)

anova(model_intercept, model_slope)  # Likelihood ratio test for nested models

```

#--------------

#Bootstrapping

##TIME:

####(To get filtered_data)
```{r}
data_all <- data_og_cwc %>% 
  filter(time == "md") 

# Filter for trees measured "before leafout"
before_leafout_data <- data_all %>%
  filter(time_season == "before leafout")

# Filter for trees measured "after leafout"
after_leafout_data <- data_all %>%
  filter(time_season == "after leafout")

# Find the common set of trees that appear in both datasets
common_trees <- intersect(before_leafout_data$tree, after_leafout_data$tree)

# Filter the original dataset to include only the common trees
common_trees_data <- data_all %>%
  filter(tree %in% common_trees)

# Assuming you have the 'common_trees_data' dataframe

# Get the unique tree IDs in 'common_trees_data'
unique_tree_ids <- unique(common_trees_data$tree)

# Count the number of unique tree IDs
num_unique_tree_ids <- length(unique_tree_ids)

# Print the number of unique tree IDs
cat("Number of unique tree IDs in common_trees_data:", num_unique_tree_ids, "\n")

# Filter the original dataset to include only the common tree IDs
filtered_data <- data_all[data_all$tree %in% common_trees, ]
```


```{r}
plotly::ggplotly(filtered_data %>% 
  drop_na(week)  %>% 
  group_by(tree) %>% 
  mutate(COUNT = n()) %>% 
  filter(!(COUNT == 1)) %>% 
  select(-COUNT) %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE, 
             label = tree)) +
  geom_point(size = 1,
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "cwc", 
       y = "Midday MPa") +
  #color_two_grey +
  theme(
      legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
  facet_wrap(~time, nrow = 2) +
  color_two_grey)
```

Pull 40 trees, get mean slope for those 40, do 1000x. 



```{r}
###Before leafout: 

data <- filtered_data  %>% 
  filter(time_season == "before leafout") %>% 
  distinct() %>% 
  drop_na(water_potential, cwc) %>% 
  group_by(tree) %>% 
  mutate(COUNT = n()) %>% 
  filter(!(COUNT == 1)) %>% 
  select(-COUNT)
data

num_unique_trees <- length(unique(data$tree))
cat("Number of unique trees in the dataset:", num_unique_trees, "\n")

# Assuming your dataset is called 'data'
# Make sure 'data' is properly loaded before proceeding

# Define the number of bootstrap iterations
n_iterations <- 1000

# Number of random trees to sample
n_sample_trees <- num_unique_trees   # Adjust as needed based on the number of unique trees

# Create an empty data frame to store bootstrapped slopes
bootstrapped_slopes_df <- data.frame()

# Function to calculate the slope for a specific tree within each iteration
calculate_slope_for_tree <- function(tree_data) {
  model <- lm(water_potential ~ cwc, data = tree_data)
  return(coef(model)[2])  # Extract the slope coefficient
}

#Do the bootstrapping: 

 for (i in 1:n_iterations) {
   
# Randomly sample 'n_sample_trees' trees from your dataset
sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE)

# Iterate through each sampled tree and perform bootstrapping separately
      for (tree_id in sampled_tree_ids) {
        
        tree_data <- data %>%
          filter(tree == tree_id)
        
        # Initialize a container to store slopes for each iteration
        slopes <- vector("double", length = 1)
      
          # Calculate the slope for the bootstrapped sample
          slopes[] <- calculate_slope_for_tree(tree_data)
        
        # Store the bootstrapped slopes for this tree in the data frame
        bootstrapped_slopes_df <- bind_rows(
          bootstrapped_slopes_df,
          data.frame(
            tree = tree_id,
            slope = slopes, 
            round = i
          ) 
        ) 
      }
 }

        ci_values <- bootstrapped_slopes_df %>%
        group_by(round) %>% 
        drop_na(slope) %>%
       mutate(
          mean_slope_round = mean(slope, na.rm = T)
        ) %>% 
          ungroup() %>% 
          mutate(mean = mean(mean_slope_round, na.rm = T),
          lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE),
          upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE))
          
        
        # Merge the CI values back into the original dataframe
      tbootstrapped_slopes_df_before <- ci_values 
      
# Print the updated dataframe with CI values
print(tbootstrapped_slopes_df_before)

summary(tbootstrapped_slopes_df_before)

mean_slope_before = tbootstrapped_slopes_df_before %>% 
  mutate(mean_slope = mean(mean, na.rm = T),
         pre_post = "before leafout") %>% 
  select(mean_slope, lower_bound, upper_bound, pre_post) %>% 
  distinct()
mean_slope_before


###After leafout: 

data <- common_trees_data %>% 
  filter(time_season == "after leafout") %>% 
  select(tree, week, water_potential, cwc) %>% 
  distinct() %>% 
  drop_na(water_potential, cwc) %>% 
  group_by(tree) %>% 
  mutate(COUNT = n()) %>% 
  filter(!(COUNT == 1)) %>% 
  select(-COUNT) 

num_unique_trees <- length(unique(data$tree))
cat("Number of unique trees in the dataset:", num_unique_trees, "\n")

# Assuming your dataset is called 'data'
# Make sure 'data' is properly loaded before proceeding

# Define the number of bootstrap iterations
n_iterations <- 1000

# Number of random trees to sample
n_sample_trees <- num_unique_trees   # Adjust as needed

# Create an empty data frame to store bootstrapped slopes
bootstrapped_slopes_df <- data.frame()

# Function to calculate the slope for a specific tree within each iteration
calculate_slope_for_tree <- function(tree_data) {
  model <- lm(water_potential ~ cwc, data = tree_data)
  return(coef(model)[2])  # Extract the slope coefficient
}

#Do the bootstrapping: 

 for (i in 1:n_iterations) {
   
# Randomly sample 'n_sample_trees' trees from your dataset
sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE)

# Iterate through each sampled tree and perform bootstrapping separately
      for (tree_id in sampled_tree_ids) {
        
        tree_data <- data %>%
          filter(tree == tree_id)
        
        # Initialize a container to store slopes for each iteration
        slopes <- vector("double", length = 1)
      
          # Calculate the slope for the bootstrapped sample
          slopes[] <- calculate_slope_for_tree(tree_data)
        
        # Store the bootstrapped slopes for this tree in the data frame
        bootstrapped_slopes_df <- bind_rows(
          bootstrapped_slopes_df,
          data.frame(
            tree = tree_id,
            slope = slopes, 
            round = i
          ) 
        ) 
      }
 }

        ci_values <- bootstrapped_slopes_df %>%
        group_by(round) %>% 
        drop_na(slope) %>%
       mutate(
          mean_slope_round = mean(slope, na.rm = T)
        ) %>% 
          ungroup() %>% 
          mutate(mean = mean(mean_slope_round, na.rm = T),
          lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE),
          upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE))
          
        
        # Merge the CI values back into the original dataframe
      tbootstrapped_slopes_df_after <- ci_values 
      
# Print the updated dataframe with CI values
print(tbootstrapped_slopes_df_after)

summary(tbootstrapped_slopes_df_after)

mean_slope_after = tbootstrapped_slopes_df_after %>% 
  mutate(mean_slope = mean(mean, na.rm = T),
         pre_post = "after leafout") %>% 
  select(mean_slope, lower_bound, upper_bound, pre_post) %>% 
  distinct()
mean_slope_after

#Combining before and after: 


cwc_time_boot_df <- bind_rows(mean_slope_before, mean_slope_after) %>% 
  select(pre_post, mean_slope, lower_bound, upper_bound) %>% 
  distinct() %>% 
  mutate(analysis = "time, ind. tree")

cwc_time_boot_df %>% 
  group_by(pre_post) %>% 
  mutate(tree_mean = mean(mean_slope, na.rm = T)) %>% 
  ggplot() +
  geom_point(aes(y = tree_mean, 
             x = pre_post)) +
  geom_point(aes(y = upper_bound, 
                 x= pre_post), color = "blue")  +
  geom_point(aes(y = lower_bound, 
                 x= pre_post), color = "pink")  +
  theme_minimal()
```

#SPACE: 
####***Slopes, MD, NOT Centered

Get slopes from random effects: 

NOTE: this includes site random effect, which the centered version does not need. 

```{r}
space_nice <- data_og_cwc %>% 
  filter(time == "md") %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
            # x = cwc_centered, 
            x = cwc,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = 1, 
            # aes (shape = site)
             ) +
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_text(size = 20), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 2))
space_nice
```


```{r}
data <- data_og_cwc %>% 
  filter(time == "md") %>% 
  select(tree, week, water_potential, cwc, site) %>% 
  distinct() %>% 
  drop_na(cwc, water_potential)

#HOW MANY trees? 

data %>% 
  drop_na(water_potential, cwc) %>% 
  group_by(week, site) %>% 
  count()

#model without site: 
space_mod_4 <- lmer(water_potential ~ cwc + (cwc|week), data =  data , REML = T)

space_mod_df_4 <- broom.mixed::tidy(space_mod_4)
#space_mod_df

ran_list3 <- coef(space_mod_4)

#ran_list2 <- coef(m_wk_rand)

ran_df_4 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`, 
         -cwc) %>%
  select(-`(Intercept)`)

ran_err_4 <- arm::se.ranef(space_mod_4)

ran_err_df_4 <- as.data.frame(ran_err_4[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`)%>% 
  select(-`(Intercept)`, 
         -cwc) %>% 
  tibble::rownames_to_column("week")

ran_df_week_4 <- bind_cols(ran_df_4, ran_err_df_4) %>% 
  #select(-`1:10`) %>% 
  data_frame()

final_df_space_se <- ran_df_week_4 

space_slope <- final_df_space_se %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = slope + 1.96*(std.error.slope), 
         lwr = slope - 1.96*(std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope - space") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_blank(),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
space_slope
```


```{r}
# Define the number of bootstrap iterations
n_iterations <- 1000

# Create an empty dataframe to store results
cwc_final_df_space <- data.frame(week = integer(), mean_slope = numeric(), lower_bound = numeric(), upper_bound = numeric())

# Get unique weeks in your dataset
unique_weeks <- unique(data$week)

# Iterate through each week
for (x in unique_weeks) {
  # Step 1: Filter data for the current week
  week_data <- data %>%
    filter(week == x)
  
  # Step 2: Initialize a container to store bootstrapped slopes
  slopes <- vector("double", length = n_iterations)
  
  # Step 3: Perform bootstrapping to estimate slopes
  for (i in 1:n_iterations) {
    # Randomly sample rows with replacement
    boot_indices <- sample(nrow(week_data), replace = TRUE)
    boot_sample <- week_data[boot_indices, ]
    
    # Calculate the slope for the bootstrapped sample
    model <- lm(water_potential ~ cwc, data = boot_sample)
    slopes[i] <- coef(model)[2]
  }
  
  # Step 4: Calculate the mean slope and 95% CI
  mean_slope <- mean(slopes, na.rm = TRUE)
  lower_bound <- quantile(slopes, 0.025, na.rm = TRUE)
  upper_bound <- quantile(slopes, 0.975, na.rm = TRUE)
  
  # Step 5: Store the results in the final dataframe
  cwc_final_df_space <- bind_rows(cwc_final_df_space, 
                                  data.frame(week = x, 
                                             mean_slope = mean_slope,
                                             lower_bound = lower_bound, 
                                             upper_bound = upper_bound))
}

# Print the final dataframe
print(cwc_final_df_space)

cwc_final_df_space %>% 
  ggplot(aes(x = week)) +
   geom_segment(aes(y= lower_bound, 
                   yend = upper_bound, 
                   x = week, 
                   xend = week, 
                   color = as.factor(week)))+
  geom_point(aes(y = mean_slope), color = "cyan") +
  geom_point(aes(y = lower_bound), color = "pink") +
  geom_point(aes(y = upper_bound), color = "gold") +
  geom_hline(yintercept =0) +
  labs(y = "Slope",
       x = "Week")
  
```

#COMBINE

Should be week, mean_slope, lower_bound, upper_bound

```{r}
cwc_final_df_space <- cwc_final_df_space %>% 
  mutate(analysis = "space", 
         time_season = "NA")

cwc_time_boot_df <- cwc_time_boot_df %>% 
  mutate(week = 0,
         time_season = pre_post)

final_df_all_cwc <- bind_rows(cwc_final_df_space, cwc_time_boot_df) %>% 
  mutate(slope = mean_slope, 
         lwr = lower_bound, 
         upr = upper_bound) 

final_df_all_cwc %>% write_csv(here::here("processed-data", "bootstrapped_df_qudo_cwc.csv"))
```
#------------

#START HERE to skip bootstrapping: 
```{r}
final_df_all_cwc <- read_csv(here::here("processed-data", "bootstrapped_df_qudo_cwc.csv"))
```

#------------

#Analysis: 

#Data wrangling: 

```{r, echo=F}
wc_qudo_df <- data_og_cwc %>% 
  drop_na(time)

wc_lm_df <- wc_qudo_df %>% 
  filter(week > 17)

wk_all <- wc_qudo_df 

wk_all_wide <- wk_all %>% 
  #drop_na(date_wp) %>% 
  pivot_wider(names_from=time, 
              values_from = c(cwc, water_potential)) %>% 
    dplyr::group_by(tree, week) %>%
  fill(c(cwc_md, cwc_pd, water_potential_pd, water_potential_md), .direction = "downup") %>%
  dplyr::ungroup()%>% 
 # select(-date_wp) %>% 
  distinct()

wk_all_long_cwc <- wk_all_wide %>% 
  drop_na(cwc_pd, cwc_md, water_potential_md, water_potential_pd) %>% 
  select(-water_potential_md, -water_potential_pd) %>% 
  mutate(pd = cwc_pd, 
         md = cwc_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "cwc") %>% 
  select(-cwc_pd, -cwc_md)

wk_all_long_mpa <- wk_all_wide %>% 
  drop_na(cwc_pd, cwc_md, water_potential_md, water_potential_pd) %>% 
  select(-cwc_md, -cwc_pd) %>% 
  mutate(pd = water_potential_pd, 
         md = water_potential_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "water_potential") %>% 
  select(-water_potential_pd, -water_potential_md)

wk_all_long <- merge(wk_all_long_mpa, wk_all_long_cwc) %>% 
  distinct() %>% 
 # select(-cwc_NA, -water_potential_NA) %>% 
  group_by(tree, week, time) %>% 
  summarise(cwc = mean(cwc, na.rm = T), 
            water_potential = mean(water_potential, na.rm = T), 
            site = site)
```


#SPACE:

1. Center and scale by week
2. Plot all midday grand slopes

###Midday: 

```{r, warning = F}
wc_wk_centered_df <- wk_all_long %>% 
  mutate(water_potential = water_potential) %>% 
  filter(time == "md") %>% 
  group_by(week) %>% 
  mutate(mean_cwc = mean(cwc, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(cwc_centered = cwc - mean_cwc)
  # mutate(cwc_centered = scale(cwc,  scale=FALSE)) %>% 
  # filter(cwc_centered < 4)
```


```{r, warning = F, echo=FALSE}
#scaled
space_nice <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
            # x = cwc_centered, 
            x = cwc,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_text(size = 20), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 2))
space_nice

ggsave(here("figures", "nice_space_cwc"), space_nice, device = "jpg", width = 6, height = 4, dpi = 300)
```

```{r, warning = F, echo=FALSE}
#scaled
space_nice_centered <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = cwc_centered, 
            #x = cwc,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="top",
        #legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Centered Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 1))

space_nice_centered

ggsave(here("figures", "nice_space_centered"), space_nice_centered, device = "jpg", width = 6, height = 4, dpi = 300)
```

Do we need to include site here? 

Centered cwc:

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ cwc_centered + (cwc_centered|week), data = space_df_nosite, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ cwc_centered  + (cwc_centered|week) + (1|site), data = space_df_nosite,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

YES

cwc uncentered:

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ cwc + (cwc|week), data = space_df_nosite, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ cwc  + (cwc|week) + (1|site), data = space_df_nosite,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```
NO


Visualize: 

###Slopes, MD, Centered:

Get slopes from random effects: 

```{r, echo=FALSE}
space_mod <- lmer(water_potential ~ (cwc_centered|week) + (1|site), data =  wc_wk_centered_df, REML = T)

space_mod_df <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_df3 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc_centered`, 
         -cwc_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)

ran_err_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc_centered`)%>% 
  select(-`(Intercept)`, 
         -cwc_centered) %>% 
  tibble::rownames_to_column("week") %>% 
  mutate(week = as.numeric(week))

# weeks_check <- list(unique(space_df$week)) #%>% as_data_frame() 
# weeks_check

# weeks <- data_frame(1:10)
# weeks$week <- c(9, 10, 14, 15, 17, 18, 19, 21, 29, 33) 

ran_df_week_3 <- bind_cols(ran_df3, ran_err_df) %>% 
  #select(-`1:10`) %>% 
  data_frame()

ran_df_week_3 %>% 
 # mutate(week = as.factor(week)) %>% 
  mutate(week = as.numeric(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
      axis.title.x = element_blank(),
  axis.title.y = element_text(size = 20), 
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
  color_grad +
   # color_many_2 +
  guides(color = guide_legend(nrow = 2))
```

Intercepts - centered

```{r, echo=FALSE}
ran_df_week_3 %>% 
   mutate(week = as.numeric(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
    color_grad +
  guides(color = guide_legend(nrow = 2))
```

##Slopes, MD, NOT Centered

Get slopes from random effects: 

NOTE: this includes site random effect, which the centered version does not need. 

```{r, echo=FALSE}
space_mod_4 <- lmer(water_potential ~ cwc + (cwc|week) + (1|site), data =  wc_wk_centered_df, REML = T)

space_mod_df_4 <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod_4)

#ran_list2 <- coef(m_wk_rand)

ran_df_4 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`, 
         -cwc) %>%
  select(-`(Intercept)`)

ran_err_4 <- arm::se.ranef(space_mod_4)

ran_err_df_4 <- as.data.frame(ran_err_4[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`)%>% 
  select(-`(Intercept)`, 
         -cwc) %>% 
  tibble::rownames_to_column("week")

ran_df_week_4 <- bind_cols(ran_df_4, ran_err_df_4) %>% 
  #select(-`1:10`) %>% 
  data_frame()

space_slope <- ran_df_week_4 %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope - space") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_blank(),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
space_slope
```
Intercept - not centered

```{r, echo=FALSE}
ran_df_week_4 %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
```


#Which weeks are significant?

```{r}
mod <- lmer(water_potential ~ cwc*week + (1|site), data =wc_wk_centered_df %>% 
              mutate(week = as.factor(week)))

anova(mod)

library("lmerTest")
summary(mod)

library(emmeans)
emmeans(mod, list(pairwise ~ week), adjust = "tukey")
```

```{r}
unique(wc_wk_centered_df$week)

#week 10: 
wk <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  mutate(week = as.factor(week)) %>% 
  filter(week == 10)

space_mod <- lmer(water_potential ~ cwc + (1|site), data =  wk,  REML = T)
summary(space_mod)
#not sig

#week 12: 
wk <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  mutate(week = as.factor(week)) %>% 
  filter(week == 12)

space_mod <- lmer(water_potential ~ cwc + (1|site), data =  wk,  REML = T)
summary(space_mod)
#not sig

#week 14: 
wk <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  mutate(week = as.factor(week)) %>% 
  filter(week == 14)

space_mod <- lm(water_potential ~ cwc, data =  wk)
summary(space_mod)
#not sig

#week 15: 
wk <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  mutate(week = as.factor(week)) %>% 
  filter(week == 15)

space_mod <- lm(water_potential ~ cwc, data =  wk)
summary(space_mod)
#not sig

#week 17: 
wk <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  mutate(week = as.factor(week)) %>% 
  filter(week == 17)

space_mod <- lm(water_potential ~ cwc, data =  wk)
summary(space_mod)
#not sig

#week 19: 
wk <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  mutate(week = as.factor(week)) %>% 
  filter(week == 19)

space_mod <- lm(water_potential ~ cwc, data =  wk)
summary(space_mod)
#sig, p = 0.008

#week 21: 
wk <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  mutate(week = as.factor(week)) %>% 
  filter(week == 21)

space_mod <- lm(water_potential ~ cwc, data =  wk)
summary(space_mod)
#not sig



#week 37: 
wk <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  mutate(week = as.factor(week)) %>% 
  filter(week == 37)

space_mod <- lmer(water_potential ~ cwc  + (1|site), data =  wk,  REML = T)
summary(space_mod)
#not sig
```

###Slopes, from bootsrapping: 

```{r}
space_slopes <- final_df_all_cwc %>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "space") %>% 
   mutate(week = as.factor(week)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope - space") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_blank(),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
space_slopes
```

#TIME

```{r}
wc_qudo_df %>% 
  drop_na(week) %>% 
  ggplot(aes(y = cwc, 
             x = as.factor(week), 
             fill = time)) +
  geom_boxplot() +
 # facet_wrap(~time) +
  color_many +
  color_fill +
  labs(y = "cwc", 
       x = "Week", 
       fill = "Time")
```

```{r, echo=FALSE, warning = F}
time <- wc_qudo_df %>% 
  drop_na(week) %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE)) +
  geom_point(size = 1,
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "cwc", 
       y = "Midday MPa") +
  #color_two_grey +
  theme(
      legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
  facet_wrap(~time, nrow = 2) +
  color_two_grey
time 

ggsave(here("figures", "nice_time"), time, device = "jpg", width = 4, height = 2, dpi = 300)
```



```{r, echo=FALSE}
wc_qudo_df %>% 
  filter(time == "pd") %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .2)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "cwc", 
       y = "Predawn MPa") +
  #color_very_many +
  theme(legend.position = "none")
```
Midday slopes for each individual: 

All dates: 

Include site?

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree), data = space_df_nosite, REML = F)
#summary(space_mod)
AIC(space_mod)

space_mod_site <- lmer(water_potential ~ cwc  + (1|week) + (cwc|tree) + (1|site), data = space_df_nosite,  REML = F)

AIC(space_mod_site)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```
YES
####All time



```{r}
wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md")

#with separate periods: 
time_season_mod <- lmer(water_potential ~ cwc + time_season + (1|week) + (cwc|tree)+ (1|site), data = wc_qudo_md_df)

time_season_mod_df <- broom::tidy(time_season_mod)

#with separate periods: 
time_season_mod_int <- lmer(water_potential ~ cwc*time_season + (1|week) + (cwc|tree)+ (1|site), data = wc_qudo_md_df)

time_season_mod_int_df <- broom::tidy(time_season_mod)

time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree)+ (1|site), data = wc_qudo_md_df)
#time_mod <- lmer(water_potential ~ cwc + (cwc|tree), data = wc_qudo_md_df)
 
MuMIn::r.squaredGLMM(time_mod)

summary(time_mod)

ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = cwc
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
tree_eff

ran_err_tree1 <- arm::se.ranef(time_mod)

ran_err_tree2 <- as.data.frame(ran_err_tree1[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
        # -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

ran_df_tree <- bind_cols(tree_eff, ran_err_tree2) %>% 
  #select(-`1:47`) %>% 
  data_frame()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ cwc)") +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))# +
  #color_very_many 

ran_df_tree %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
  mutate(upr = slope + (std.error), 
         lwr = slope - (std.error)) %>% 
  ggplot(aes(color= estimate)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = estimate))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ cwc)") +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  theme(legend.position = "none", 
        axis.text.x = element_blank())#+
  #theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

####Just linear: 
```{r}
lin_wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  filter(time_season == "after leafout")
  
  
lin_time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree) + (1|site), data = lin_wc_qudo_md_df)
summary(lin_time_mod)

MuMIn::r.squaredGLMM(lin_time_mod)
```


```{r}
lin_ran_list <- coef(lin_time_mod)
lin_ran_list

lin_tree_eff <- as.data.frame(lin_ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`,
         sd = sd(slope)
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
lin_tree_eff

lin_ran_err_tree <- arm::se.ranef(lin_time_mod)

lin_ran_err_tree <- as.data.frame(lin_ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
        # -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

lin_ran_df_tree_after <- bind_cols(lin_tree_eff, lin_ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame() %>% 
  mutate(time_season = "After Leafout")

#With standard errors around estimates:

#intercetps 
lin_ran_df_tree_after%>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Intercepts, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 


lin_ran_df_tree_after %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 

lin_ran_df_tree_after %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()
```
####Before leafout: 

```{r}
bef_wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  filter(time_season == "before leafout") %>% 
  drop_na(site)
  
  
bef_time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree) + (1|site), data = bef_wc_qudo_md_df, REML = T)
summary(bef_time_mod)


MuMIn::r.squaredGLMM(bef_time_mod)
```


```{r}
bef_ran_list <- coef(bef_time_mod)

bef_tree_eff <- as.data.frame(bef_ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`, 
         sd = sd(slope)
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
bef_tree_eff

bef_ran_err_tree <- arm::se.ranef(bef_time_mod)

bef_ran_err_tree <- as.data.frame(bef_ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
         -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

bef_ran_df_tree_before <- bind_cols(bef_tree_eff, bef_ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame()%>% 
  mutate(time_season = "Before Leafout")

bef_ran_df_tree_before %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, BEFORE LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) #+
 # color_very_many 

bef_ran_df_tree_before %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()
```

####Slopes, SE, pre- and post-

```{r}
ran_df_tree_before_vs_after <- bind_rows(bef_ran_df_tree_before, lin_ran_df_tree_after)

ef <- ran_df_tree_before_vs_after %>% 
  group_by(time_season) %>% 
  mutate(sd = sd(slope),
         slope = mean(slope), 
         mean_se = mean(std.error.slope),
        mean_std.error = mean(std.error),
        upr_sd = slope + mean_std.error,
        lwr_sd = slope - mean_std.error,
         upr = slope + mean_se,
         lwr = slope - mean_se,
         time_season = as.factor(time_season)) 
# %>% 
#   select(slope, upr, lwr, time_season, sd)

time_summary <- ef %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SE acrss all trees
            for each time frame", 
       x = "Time")
time_summary

time_summary_sd <- ef %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr_sd, x = time_season), size = 1) +
  geom_point(aes(y = lwr_sd, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr_sd, 
                   yend = upr_sd, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SD acrss all trees
            for each time frame", 
       x = "Time")
time_summary_sd

ggsave(here("figures", "time_summary_slopes"), time_summary, device = "jpg", width = 2.5, height = 3, dpi = 300)
```

##Slopes, bootstrapping - inds
 
```{r}
time_summary_bs_tree <- final_df_all_cwc %>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "time, ind. tree") %>% 
   mutate(week = as.factor(week)) %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Bootstrapped slope and CI", 
       x = "Time")
time_summary_bs_tree


ggsave(here("figures", "time_summary_slopes_boot_tree"), time_summary_bs_tree, device = "jpg", width = 2.5, height = 3, dpi = 300)
```

#MODELS

```{r}
glance_df <- bind_rows(space_glance <- broom.mixed::glance(space_mod) 
                       %>% mutate(mod = "space"),
                       time_glance <- broom.mixed::glance(time_season_mod)
                       %>% mutate(mod = "time"),
                       time_glance <- broom.mixed::glance(time_season_mod_int)
                       %>% mutate(mod = "interaction"),
                       as_data_frame(r.squaredGLMM(space_mod)) 
                       %>% mutate(mod = "space"),
                       as_data_frame(r.squaredGLMM(time_season_mod)) 
                       %>% mutate(mod = "time"),
                       as_data_frame(r.squaredGLMM(time_season_mod_int)) 
                       %>% mutate(mod = "interaction")) %>% 
  group_by(mod) %>% 
  fill(c(R2m, R2c), .direction = "downup") %>% 
  distinct() %>% 
  drop_na(df.residual)
glance_df
```


```{r}
cwc_mods <- bind_rows(space_mod_df <- space_mod_df %>% mutate(mod = "space"),
                      time_season_mod_df <- time_season_mod_df %>% mutate(mod= "time"),
  time_season_mod_df <- time_season_mod_int_df %>% mutate(mod= "interaction")) %>% 
  bind_rows(glance_df) %>% 
  mutate(var = "cwc")

cwc_mods


write_csv(cwc_mods, here::here("processed-data", "model results", "cwc_mods.csv"))
```

#----------
#FIGURES


#Slopes: 

####Space - SE

```{r}
space_slope_df <- final_df_space_se%>%  
  mutate(week = case_when(
        week %in% c(10) ~ "2022-03-08",
        week %in% c(10) ~  "2022-03-15", 
        week %in% c(12) ~  "2022-03-25",
        week %in% c(14) ~  "2022-04-04",
        week %in% c(15) ~  "2022-04-11",
        week %in% c(17) ~  "2022-04-25", 
        week %in% c(18) ~ "2022-05-04",
        week %in% c(19) ~  "2022-05-09",
        week %in% c(21) ~  "2022-05-23",
        week %in% c(29) ~  "2022-07-19",
        week %in% c(33) ~  "2022-08-18",
        week %in% c(37) ~  "2022-09-15")) %>% 
  mutate(week = format(as.Date(week), "%m-%d")) %>% 
  mutate(week = as.factor(week))

unique(space_slope_df$week)
```

```{r}
# Define the weeks to highlight
highlighted_weeks <- c("05-09")  # Example weeks

space_slope <- final_df_space_se %>%  
  mutate(week = case_when(
        week %in% c(10) ~ "2022-03-08",
        week %in% c(11) ~  "2022-03-15", 
        week %in% c(12) ~  "2022-03-25",
        week %in% c(14) ~  "2022-04-04",
        week %in% c(15) ~  "2022-04-11",
        week %in% c(17) ~  "2022-04-25", 
        week %in% c(18) ~  "2022-05-04",
        week %in% c(19) ~  "2022-05-09",
        week %in% c(21) ~  "2022-05-23",
        week %in% c(29) ~  "2022-07-19",
        week %in% c(33) ~  "2022-08-18",
        week %in% c(37) ~  "2022-09-15")) %>% 
  mutate(week = format(as.Date(week), "%m-%d")) %>% 
  mutate(week = as.factor(week)) %>% 
  mutate(upr = slope + 1.96 * std.error.slope, 
         lwr = slope - 1.96 * std.error.slope, 
         is_highlighted = ifelse(week %in% highlighted_weeks, TRUE, FALSE)) %>% 
 ggplot(aes(color = as.factor(week)))  + 
  geom_point(aes(y = slope, x = week, shape = is_highlighted), size = 3) +
  geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  geom_segment(aes(y = lwr, yend = upr, x = week, xend = week, color = week)) +
  scale_shape_manual(values = c(1, 16)) + # Filled (16) and unfilled (1) points
  labs(x = "Week", color = "Week", y = " ") +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_text(size = 12),
        plot.title = element_text(size = 13),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text = element_text(size = 12),
        legend.key = element_blank(), 
        legend.text = element_text(size = 13), 
        legend.title = element_blank(),
        legend.margin = margin(0, 0, 0, 0),
        legend.box.margin = margin(-5, -8, -8, -8),
        plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt"),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = .25)) +
  geom_hline(yintercept = 0, linetype = "dotted") + 
  scale_color_manual(values = c("9" ="#122241",
                                                     "03-08" = "#48578E", #week 10
                                                    "03-15" = "#48578E", #10
                                                    # "11" = "#122451", 
                                                     "03-23" = "#165E6F", #12
                                                     "03-25" = "#165E6F", #12
                                                     "03-30" = "#B6D0E2", #14
                                                     "04-04" = "#B6D0E2", #14
                                                     "04-06" = "#B6D0E2", #14
                                                     #"13" = "#B6D0E2", 
                                                     "04-13" = "#729684", 
                                                     "04-11" = "#729684", 
                                                    # "16" = "#8E9D68", 
                                                     "04-27" = "#8E9D30", #17
                                                     "04-25" = "#8E9D30", #17
                                                    # "18" = "#D7B110",
                                                     "05-09" = "#D9C000", #19
                                                    # "20" = "#F8A63A" ,
                                                    # "21" = "#F8A63A" ,
                                                     "05-23" = "#EC7E28", #21
                                                     "07-19" = "#CC5210", #29
                                                     "08-18"= "#E97B6E", #33
                                                    # "37" = "#b33b72",
                                                     "09-15" = "#CC5265" #37
                                                     #"39" = "#862d46" 
                                                    # "39" = "#C969A1"
                                                   #  "37" = "#b33b72",
                                                   #  "39" = "#893843"
                                                    )) +
  guides(color = guide_legend(nrow = 2)) 

space_slope
```


```{r, eval = F}
space_slope <- space_slope_df %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = slope + 1.96*(std.error.slope), 
         lwr = slope - 1.96*(std.error.slope)) %>% 
 ggplot(aes(color= as.factor(week))
    )  + 
  #  geom_rect(aes(ymin = 701.6674, ymax = 1074.701, 
  #         xmin = -Inf, xmax = Inf), 
  #         fill = "#969696",
  #         alpha = .01, 
  #         color = NA) +
  # geom_hline(aes(yintercept = 880.5797), color = "#525252") +
  geom_point(aes(y = slope ,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = " ") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
    # legend.title = element_text(size = 16),
    legend.title = element_blank(),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
    plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt"),
     axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=.25)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_color_manual(values = c("9" ="#122241",
                                                     "03-08" = "#48578E", #week 10
                                                    "03-15" = "#48578E", #10
                                                    # "11" = "#122451", 
                                                     "03-23" = "#165E6F", #12
                                                     "03-25" = "#165E6F", #12
                                                     "03-30" = "#B6D0E2", #14
                                                     "04-04" = "#B6D0E2", #14
                                                     "04-06" = "#B6D0E2", #14
                                                     #"13" = "#B6D0E2", 
                                                     "04-13" = "#729684", 
                                                     "04-11" = "#729684", 
                                                    # "16" = "#8E9D68", 
                                                     "04-27" = "#8E9D30", #17
                                                     "04-25" = "#8E9D30", #17
                                                       "05-04" = "#D7B110", #18
                                                     "05-09" = "#D9C000", #19
                                                    # "20" = "#F8A63A" ,
                                                    # "21" = "#F8A63A" ,
                                                     "05-23" = "#EC7E28", #21
                                                     "07-19" = "#CC5210", #29
                                                     "08-18"= "#E97B6E", #33
                                                    # "37" = "#b33b72",
                                                     "09-15" = "#CC5265" #37
                                                     #"39" = "#862d46" 
                                                    # "39" = "#C969A1"
                                                   #  "37" = "#b33b72",
                                                   #  "39" = "#893843"
                                                    )) +
  #scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                  #   breaks = c(37, 33, 29, 21, 19, 17, 15, 14, 12, 10)
                      # seq(10, 30, by = 1)
  #                   ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  guides(color = guide_legend(nrow = 2)) #+
space_slope
```

####Space - BS
```{r}
space_slope_bs <- final_df_all_cwc %>% 
    # filter(!week %in% c(9)) %>% 
  mutate(week = case_when(
    week %in% c(10) ~ "2022-03-08",
    week %in% c(11) ~ "2022-03-15", 
    week %in% c(12) ~ "2022-03-25",
    week %in% c(14) ~ "2022-04-04",
    week %in% c(15) ~ "2022-04-11",
    week %in% c(17) ~ "2022-04-25", 
    week %in% c(19) ~ "2022-05-09",
    week %in% c(21) ~ "2022-05-23",
    week %in% c(29) ~ "2022-07-19",
    week %in% c(33) ~ "2022-08-18",
    week %in% c(37) ~ "2022-09-15")) %>%  
  filter(analysis == "space") %>% 
  mutate(week = format(as.Date(week), "%m-%d"),
         bounds_overlap_zero = (lwr <= 0 & upr >= 0)) %>%  # Check if bounds overlap 0
  filter(analysis == "space") %>% 
  ggplot(aes(color = as.factor(week))) + 
  geom_point(aes(y = slope, x = as.factor(week), shape = bounds_overlap_zero), size = 3) +  # Shape depends on overlap
  geom_point(aes(y = upr, x = as.factor(week)), size = 1) +
  geom_point(aes(y = lwr, x = as.factor(week)), size = 1) +
  geom_segment(aes(y = lwr, yend = upr, x = as.factor(week), xend = as.factor(week))) +
  labs(
    x = "Week", 
    color = "Week", 
    y = "Slope"
  ) +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text.x = element_text(size = 12),
    plot.title = element_text(size = 13),
    axis.title = element_blank(),
    axis.text = element_text(size = 12),
    legend.key = element_blank(), 
    legend.text = element_text(size = 13), 
    legend.title = element_blank(),
    legend.margin = margin(0, 0, 0, 0),
    legend.box.margin = margin(-5, -8, -8, -8),
    plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = .25)
  ) +
  geom_hline(yintercept = 0, linetype = "dotted") + 
  scale_color_manual(values = c(
    "03-08" = "#48578E", 
    "03-15" = "#48578E", 
    "03-25" = "#165E6F", 
    "04-04" = "#B6D0E2", 
    "04-11" = "#729684", 
    "04-25" = "#8E9D30", 
    "05-09" = "#D9C000", 
    "05-23" = "#EC7E28", 
    "07-19" = "#CC5210", 
    "08-18" = "#E97B6E", 
    "09-15" = "#CC5265"
  )) +
  scale_shape_manual(values = c(`TRUE` = 1, `FALSE` = 16))  # Open circle for TRUE, closed for FALSE

space_slope_bs
```

```{r, eval = F}
space_slope <-  final_df_all_cwc %>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "space") %>% 
 # mutate(week = as.numeric(week)) %>% 
   ggplot(aes(color= as.factor(week))
    ) + 
  geom_point(aes(y = slope ,x = as.factor(week)), size =2) +
    geom_point(aes(y = upr, x = as.factor(week)), size = 1) +
  geom_point(aes(y = lwr, x = as.factor(week)), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = as.factor(week), 
                   xend = as.factor(week), 
                   color = as.factor(week)))+
  labs(x = "Week", 
       color = "Week", 
       y = " ") +
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text.y = element_text(size = 12),
     axis.text.x = element_text(size = 12),
    # axis.text.x  = element_blank(),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
    plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt")
    ) +
  #scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                  #   breaks = c(37, 33, 29, 21, 19, 17, 15, 14, 12, 10)
                      # seq(10, 30, by = 1)
  #                   ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  color_week_assigned +
 # color_many_2 +
  guides(color = guide_legend(nrow = 2))
 # scale_x_reverse()
space_slope

```

####Time

BS:

```{r}
time_summary <- final_df_all_cwc%>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "time, ind. tree") %>% 
   mutate(week = as.factor(week), 
          time_season = case_when(
            time_season %in% c("before leafout") ~ "During", 
             time_season %in% c("after leafout") ~ "After", 
            
          )) %>% 
ggplot(aes(color = time_season)) + 
  geom_point(aes(y = slope, x = time_season), size =3) +
  geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "",
       x = "Time") +
  color_two_grey +
  geom_hline(yintercept = 0, linetype="dotted") + 
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text.y = element_text(size = 12),
     axis.text.x = element_text(size = 12),
    # axis.text.x  = element_blank(),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
    plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt")
    ) +
  scale_x_discrete(limit = rev)
  
time_summary
```





#*FIGURES*


#Scatterplots:

#####Space

```{r}
#scaled
space_nice_1 <- data_og_cwc %>% 
  filter(time == "md") %>% 
  select(tree, week, water_potential, cwc) %>% 
  distinct() %>% 
  drop_na(cwc, water_potential) %>% 
  ggplot(aes(y = water_potential, 
            x = cwc,
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text.y = element_text(size = 12),
     axis.text.x = element_text(size = 12),
    # axis.text.x  = element_blank(),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
    plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt")
    ) +
  geom_smooth(method = "lm", se = F,size = .5) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(#y= "Middays (MPa)", 
       y = " ",
       x = "Leaf Water per Area", 
       color = "Week", 
       shape = "Site") +
  #color_many_2 +
  color_week_assigned +
 # xlim(.5,2) +
 # ylim(-5,0)+
  guides(color = guide_legend(nrow = 2)) +
  #scale_x_reverse() +
scale_y_continuous(labels = scales::number_format(accuracy = 0.1))
space_nice_1


```
#####Time:

```{r}
time_1 <- data_og_cwc %>% 
  mutate(time = case_when(
    time == "md" ~ "Midday", 
    time == "pd" ~ "Predawn"
  )) %>% 
  filter(time == "Midday") %>% 
  drop_na(week) %>% 
 # filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE)) +
  geom_point(size = 1,
             alpha = .1)+
  geom_smooth(method = "lm", se = F, size = .5, alpha = .4) +
 # theme(legend.position = "none") +
  labs(x = "lwc_mean", 
       y = "Midday MPa") +
  #color_two_grey +
  theme(
      legend.position="none",
      strip.background = element_blank(),
     # strip.text.x = element_text(size = 12),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      #axis.title = element_text(size = 15),
     axis.title = element_blank(),
     axis.text = element_text(size = 12),
     axis.text.x = element_text(size = 12),
     legend.key=element_blank(),
     legend.text = element_text(size = 13),
     legend.title = element_text(size = 16),
     #legend.title = element_blank(),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
     plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt")
    ) +
  labs(#y= "Water Potential (MPa)", 
       y = "Water Potential (MPa)",
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
  color_two_grey +
scale_y_continuous(labels = scales::number_format(accuracy = 0.1))

time_1 
```

######Legend:

```{r}
legend_plot <- data_og_cwc  %>% 
  add_row(date_wp = as.Date("2022-05-03"), time = "md", cwc = .05, water_potential = -.3) %>% 
  filter(date_wp %in% c("2022-03-08",
         "2022-03-15", 
         "2022-03-25",
         "2022-04-04",
         "2022-04-11",
         "2022-04-25", 
         #"2022-05-04",
         "2022-05-09",
         "2022-05-23",
         "2022-07-19",
         "2022-08-18",
         "2022-09-15")) %>%
  mutate(week = format(as.Date(date_wp), "%m-%d"))  %>% 
  drop_na(site) %>% 
  mutate(time = case_when(
    time == "md" ~ "Midday", 
    time == "pd" ~ "Predawn"
  )) %>% 
  filter(time == "Midday") %>% 
  filter(!(week == 9)) %>% 
  drop_na(week) %>% 
  ggplot(aes(y = water_potential,
             x = cwc,
             color = as.factor(week), 
            # shape = as.factor(time),
             )) +
  geom_point() +
  theme(legend.position="right",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     axis.title.x = element_blank(),
     axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,.2,.2,.2),
   # legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F, size = .5) + 
  labs(color = "Date", 
       shape = "Time") +
  scale_color_manual(values = c("9" ="#122241",
                                                     "03-08" = "#122241", #week 10
                                                   # "03-15" = "#48578E", #10
                                                    # "11" = "#122451", 
                                                     "03-23" = "#165E6F", #12
                                                     "03-25" = "#165E6F", #12
                                                     "03-30" = "#B6D0E2", #14
                                                     "04-04" = "#B6D0E2", #14
                                                     "04-06" = "#B6D0E2", #14
                                                     #"13" = "#B6D0E2", 
                                                     "04-13" = "#729684", 
                                                     "04-11" = "#729684", 
                                                    # "16" = "#8E9D68", 
                                                     "04-27" = "#8E9D30", #17
                                                     "04-25" = "#8E9D30", #17
                                                    "05-04" = "#D7B110", #18
                                                     "05-09" = "#D9C000", #19
                                                    # "20" = "#F8A63A" ,
                                                    # "21" = "#F8A63A" ,
                                                     "05-23" = "#EC7E28", #21
                                                     "07-19" = "#CC5210", #29
                                                     "08-18"= "#E97B6E", #33
                                                    # "37" = "#b33b72",
                                                     "09-15" = "#CC5265" #37
                                                     #"39" = "#862d46" 
                                                    # "39" = "#C969A1"
                                                   #  "37" = "#b33b72",
                                                   #  "39" = "#893843"
                                                    )) #+
 # ylim(0,2) +
  #guides(color = guide_legend(nrow = 1))
legend_plot

legend_scatterplots <- cowplot::get_legend(legend_plot)
legend_scatterplots
```

#COMBINE

```{r}
library(grid)
#labels of slopes: 
y.grob1 <- textGrob("Slope (\U0394 \U03A8 / \U0394 CWC)",
                   gp=gpar(fontface="bold", #col="blue", 
                           fontsize=15), rot=90)

x.grob1 <- textGrob("Time", 
                   gp=gpar(fontface="bold", #col="blue", 
                           fontsize=15))

combined_slopes_wide <- cowplot::plot_grid(time_summary, NULL, space_slope_bs, 
                                           # NULL, pv_slope,
                                   nrow = 1, 
                                  rel_widths = c(1, -.005, 1  #, -.02, .5
                                                 ), 
                                  labels = c("C", "", "D"#,"", "G"
                                             ),
                                  label_x = .1,
                                  hjust= c(0, 0, 0),
                                  label_y = .98
                                  # rel_heights = c(.15, 1, .3), 
                                   #rel_widths = c(1, 1, 1), 
                                  # rel_widths = c(.7, .8, .7, .3)
                                   ) 

combined_slopes_wide

combined_slopes_wide_labels <- grid.arrange(arrangeGrob(combined_slopes_wide, 
                            left = y.grob1, 
                            bottom = x.grob1),
                            heights = c(1, .05))

#labels of scatterplots: 
y.grob2 <- textGrob("Water Potential (MPa)", 
                   gp=gpar(fontface="bold", #col="blue", 
                           fontsize=15), rot=90)

x.grob2 <- textGrob("Canopy Water Content (g/cm2)", 
                   gp=gpar(fontface="bold", #col="blue",
                           fontsize=15))


combined_plots_wide_nolegend <- cowplot::plot_grid(
                                      time_1,
                                      NULL, 
                                      space_nice_1, 
                                   labels=c("A","", "B"),
                                   label_x = .1,
                                   label_y = .98,
                                   nrow = 1,
                                   rel_widths = c(1, -0, 1)
                                   #rel_widths = c(1, 1, 1)
                                   ) 
combined_plots_wide_nolegend

combined_plots_wide <- cowplot::plot_grid(combined_plots_wide_nolegend,
                                      legend_scatterplots,
                                          nrow = 1, 
                                          rel_heights = c(1, 1))

combined_plots_wide_labels <- grid.arrange(arrangeGrob(combined_plots_wide_nolegend,
                                left = y.grob2, 
                                bottom = x.grob2,
                               # right = legend_scatterplots,
                                heights = c(1, 0)))
combined_plots_wide_labels 

combined_plots_all <- cowplot::plot_grid(
  combined_plots_wide_labels, 
  combined_slopes_wide_labels, 
          nrow = 2, 
          rel_heights = c(.75, .6))

combined_plots_all

combined_plots_all_legend <- grid.arrange(arrangeGrob(combined_plots_all,
                                right = legend_scatterplots,
                                heights = c(1, 0), 
                                widths = c(1, .02)))
combined_plots_all_legend

ggsave(here("figures", "qudo figures", "CWC", "combined_plots_all_qudo_bs"), combined_plots_all_legend, device = "jpg", width = 10, height = 7, dpi = 300)
```

#-----------------

<!-- #dCWC (change in CWC over time) -->


<!-- #FIGURE over time -->

<!-- ```{r} -->
<!-- filtered_data %>%  -->
<!--   ggplot(aes(y = cwc, x = week, color = as.factor(tree))) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = F) -->
<!-- ``` -->

<!-- #####Whole time period after leaf expansion (April 25, May 04, May 09, May 23, Sept. 15) -->
<!-- ```{r} -->
<!-- ###dcwc leafout:  -->
<!-- ##Get trees that have at least 2 measurements:  -->
<!-- data <- filtered_data %>%  -->
<!--   filter(time_season == "after leafout") %>%  -->
<!--   distinct() %>%  -->
<!--   drop_na(cwc) %>%  -->
<!--   group_by(tree) %>%  -->
<!--   mutate(COUNT = n()) %>%  -->
<!--   filter(!(COUNT == 1)) %>%  -->
<!--   select(-COUNT)  %>% -->
<!--   filter( -->
<!--     sum(format(date_wp, "%m") == "05") > 0,  # At least one measurement in May -->
<!--     sum(format(date_wp, "%m") == "09") > 0,  # At least one measurement in September -->
<!--     n() >= 2  # At least two measurements -->
<!--   ) %>% -->
<!--   ungroup() -->
<!-- data -->
<!-- unique(data$date_wp) -->

<!-- data %>%  -->
<!--   ggplot(aes(y = cwc, x = date_wp, color = as.factor(tree))) +  -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = F) -->

<!-- unique(data$date_wp) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- #How many unique trees did we sample across these time periods? 39! -->
<!-- num_unique_trees <- length(unique(data$tree)) -->
<!-- cat("Number of unique trees in the dataset:", num_unique_trees, "\n") -->

<!-- #Code to run the bootstrapping in parallel (from ChatGPT): -->

<!-- # Assuming your dataset is called 'data' -->
<!-- # Make sure 'data' is properly loaded dcwc proceeding -->
<!-- # Load necessary libraries -->
<!-- library(tidyverse) -->
<!-- library(parallel) -->

<!-- # Define the number of bootstrap iterations -->
<!-- n_iterations <- 1000 -->

<!-- # Number of random trees to sample -->
<!-- n_sample_trees <- 39  # Adjust as needed based on the number of unique trees -->

<!-- # Function to calculate the slope for a specific tree within each iteration -->
<!-- calculate_slope_for_tree <- function(tree_data) { -->
<!--   model <- lm(cwc ~ week, data = tree_data) -->
<!--   return(coef(model)[2])  # Extract the slope coefficient -->
<!-- } -->

<!-- # Function to perform a single bootstrap iteration -->
<!-- perform_bootstrap <- function(i, data, n_sample_trees) { -->
<!--   # Randomly sample 'n_sample_trees' trees with replacement -->
<!--   sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE) -->

<!--   # Calculate slopes for each sampled tree and store the results -->
<!--   bootstrapped_slopes <- lapply(sampled_tree_ids, function(tree_id) { -->
<!--     tree_data <- data %>% filter(tree == tree_id) -->
<!--     slope <- calculate_slope_for_tree(tree_data) -->
<!--     data.frame(tree = tree_id, slope = slope, round = i) -->
<!--   }) -->

<!--   # Combine the list of data frames into a single data frame -->
<!--   do.call(bind_rows, bootstrapped_slopes) -->
<!-- } -->

<!-- # Run the bootstrapping in parallel -->
<!-- bootstrapped_slopes_list <- mclapply(1:n_iterations, function(i) { -->
<!--   perform_bootstrap(i, data, n_sample_trees) -->
<!-- }, mc.cores = detectCores() - 1) -->

<!-- # Combine all bootstrap results into a single data frame -->
<!-- bootstrapped_slopes_df <- bind_rows(bootstrapped_slopes_list) -->

<!-- # Calculate CI values -->
<!-- ci_values <- bootstrapped_slopes_df %>% -->
<!--   group_by(round) %>% -->
<!--   drop_na(slope) %>% -->
<!--   mutate(mean_slope_round = mean(slope, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   summarize( -->
<!--     mean = mean(mean_slope_round, na.rm = TRUE), -->
<!--     lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE), -->
<!--     upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE) -->
<!--   ) -->

<!-- # Print the CI values -->
<!-- print(ci_values) -->

<!-- # Calculate overall mean slope and add "pre_post" column -->
<!-- mean_slope_dcwc <- ci_values %>% -->
<!--   mutate(mean_slope = mean(mean, na.rm = TRUE), pre_post = "dcwc leafout") %>% -->
<!--   select(mean_slope, lower_bound, upper_bound, pre_post) %>% -->
<!--   distinct() -->

<!-- print(mean_slope_dcwc) -->

<!-- # Merge unique slope results with the original dataset -->
<!-- dcwc_space <- bootstrapped_slopes_df %>% -->
<!--   select(tree, slope) %>% -->
<!--   distinct() -->

<!-- # Assuming 'data_og_cwc' is defined in your environment -->
<!-- dcwc_df <- merge(dcwc_space, data_og_cwc) -->

<!-- # Calculate the IQR bounds for the slope column -->
<!-- slope_bounds <- dcwc_df %>% -->
<!--   summarize( -->
<!--     lower_bound = quantile(slope, 0.25) - 1.5 * IQR(slope), -->
<!--     upper_bound = quantile(slope, 0.75) + 1.5 * IQR(slope) -->
<!--   ) -->
<!-- # Print the final merged dataframe -->
<!-- print(dcwc_df) -->

<!-- plotly::ggplotly(dcwc_df %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = week,  -->
<!--                               color = time)) + -->
<!--                    geom_point() +  -->
<!--                    geom_smooth(method = "lm")  -->
<!--                    #facet_wrap(~week, scales = "free") -->
<!--                  ) -->

<!-- dcwc_df %>%  -->
<!--   filter(week > 19) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = water_potential,  -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "Water Potential (MPa)",  -->
<!--        color = "Time") -->

<!-- # Calculate the IQR bounds for the slope column -->
<!-- slope_bounds <- dcwc_df %>% -->
<!--   summarize( -->
<!--     lower_bound = quantile(slope, 0.25) - 1.5 * IQR(slope), -->
<!--     upper_bound = quantile(slope, 0.75) + 1.5 * IQR(slope) -->
<!--   ) -->

<!-- # Filter out rows where slope falls outside of these bounds -->
<!-- dcwc_df_no_outliers <- dcwc_df %>% -->
<!--   filter(slope >= slope_bounds$lower_bound & slope <= slope_bounds$upper_bound) -->

<!-- # Print the cleaned dataset without outliers -->
<!-- print(dcwc_df_no_outliers) -->

<!-- plotly::ggplotly(dcwc_df_no_outliers %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = week,  -->
<!--                               color = time)) + -->
<!--                    geom_point() +  -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    facet_wrap(~week, scales = "free") -->
<!--                  ) -->

<!-- dcwc_df_no_outliers %>%  -->
<!--   #filter(week > 19) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = water_potential,  -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "Water Potential (MPa)",  -->
<!--        color = "Time") -->

<!-- #Are any of the weeks significant? -->

<!-- # Ensure columns are numeric and filter out NAs -->
<!-- filtered_data <- dcwc_df_no_outliers %>% -->
<!--  # filter(week > 19) %>% -->
<!--   mutate( -->
<!--     water_potential = as.numeric(water_potential), -->
<!--     slope = as.numeric(slope) -->
<!--   ) %>% -->
<!--   drop_na(water_potential, slope) # Remove rows with NA in these columns -->

<!-- # Fit a linear model for each date and time combination, then extract p-values and slope estimates -->
<!-- model_results <- filtered_data %>% -->
<!--   group_by(date_wp, time) %>% -->
<!--   group_modify(~ tidy(lm(water_potential ~ slope, data = .x))) %>% -->
<!--   filter(term == "slope") %>% -->
<!--   select(date_wp, time, estimate, std.error, statistic, p.value) -->

<!-- # View the results -->
<!-- print(model_results) -->

<!-- model_results %>%  -->
<!--   filter(p.value < 0.1) -->

<!-- # View the results -->
<!-- print(model_results) -->

<!-- sig_mods_whole_mpa <- model_results %>%  -->
<!--   filter(p.value < 0.05)  -->
<!-- sig_mods_whole_mpa -->

<!-- dcwc_df_no_outliers %>% -->
<!--   filter((date_wp %in% c(sig_mods_whole_mpa$date_wp) & time %in% c(sig_mods_whole_mpa$time))) %>% -->
<!--                    ggplot(aes(y = slope, -->
<!--                               x = water_potential, -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() + -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC", -->
<!--        x = "Water Potential (MPa)", -->
<!--        color = "Time") -->
<!-- ``` -->


<!-- ```{r} -->
<!-- ##ADD LMA -->

<!-- filtered_data_lma <- merge(data_qudo_lma, filtered_data, by = c("tree", "week"), all = T) %>%  -->
<!--   select(-water_potential.x, -water_potential.y) %>%  -->
<!--   distinct() %>% -->
<!--  # filter(week > 19) %>% -->
<!--   mutate( -->
<!--     lma_g_cm2 = as.numeric(lma_g_cm2), -->
<!--     slope = as.numeric(slope) -->
<!--   ) %>% -->
<!--   drop_na(lma_g_cm2, slope) %>%  -->
<!--   select(tree, week, date_wp, slope, lma_g_cm2) -->

<!-- # Fit a linear model for each date and time combination, then extract p-values and slope estimates -->
<!-- model_results_lma <- filtered_data_lma %>% -->
<!--   group_by(date_wp) %>% -->
<!--   group_modify(~ tidy(lm(lma_g_cm2 ~ slope, data = .x))) %>% -->
<!--   filter(term == "slope") %>% -->
<!--   select(date_wp,  estimate, std.error, statistic, p.value) -->

<!-- # View the results -->
<!-- print(model_results_lma) -->

<!-- model_results_lma %>%  -->
<!--   filter(p.value < 0.1) -->

<!-- # View the results -->
<!-- print(model_results_lma) -->

<!-- sig_mods_whole_lma <- model_results_lma %>%  -->
<!--   filter(p.value < 0.05)  -->
<!-- sig_mods_whole_lma -->

<!-- filtered_data_lma %>%  -->
<!--   filter((date_wp %in% c(sig_mods_whole_lma$date_wp))) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = lma_g_cm2)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "LMA (g/cm2)",  -->
<!--        color = "Time") -->

<!-- dcwc_df_no_outliers %>% write_csv(here("processed-data", "dcwc_afterleafout_df_no_outliers.csv")) -->

<!-- ``` -->

<!-- Early season:  -->

<!-- #####Before leafout: -->
<!-- ```{r} -->
<!-- ###dcwc leafout:  -->
<!-- ##Get trees that have at least 2 measurements:  -->
<!-- data <- filtered_data  %>%  -->
<!--   filter(time_season == "before leafout") %>%  -->
<!--   distinct() %>%  -->
<!--   drop_na(cwc) %>%  -->
<!--   group_by(tree) %>%  -->
<!--   mutate(COUNT = n()) %>%  -->
<!--   filter(!(COUNT == 1)) %>%  -->
<!--   select(-COUNT) -->
<!-- data -->

<!-- unique(data$date_wp) -->

<!-- data %>%  -->
<!--   ggplot(aes(y = cwc, x = date_wp, color = as.factor(tree))) +  -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = F) -->

<!-- #How many unique trees did we sample across these time periods? 39! -->
<!-- num_unique_trees <- length(unique(data$tree)) -->
<!-- cat("Number of unique trees in the dataset:", num_unique_trees, "\n") -->

<!-- #Code to run the bootstrapping in parallel (from ChatGPT): -->

<!-- # Assuming your dataset is called 'data' -->
<!-- # Make sure 'data' is properly loaded dcwc proceeding -->
<!-- # Load necessary libraries -->
<!-- library(tidyverse) -->
<!-- library(parallel) -->

<!-- # Define the number of bootstrap iterations -->
<!-- n_iterations <- 1000 -->

<!-- # Number of random trees to sample -->
<!-- n_sample_trees <- 39  # Adjust as needed based on the number of unique trees -->

<!-- # Function to calculate the slope for a specific tree within each iteration -->
<!-- calculate_slope_for_tree <- function(tree_data) { -->
<!--   model <- lm(cwc ~ week, data = tree_data) -->
<!--   return(coef(model)[2])  # Extract the slope coefficient -->
<!-- } -->

<!-- # Function to perform a single bootstrap iteration -->
<!-- perform_bootstrap <- function(i, data, n_sample_trees) { -->
<!--   # Randomly sample 'n_sample_trees' trees with replacement -->
<!--   sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE) -->

<!--   # Calculate slopes for each sampled tree and store the results -->
<!--   bootstrapped_slopes <- lapply(sampled_tree_ids, function(tree_id) { -->
<!--     tree_data <- data %>% filter(tree == tree_id) -->
<!--     slope <- calculate_slope_for_tree(tree_data) -->
<!--     data.frame(tree = tree_id, slope = slope, round = i) -->
<!--   }) -->

<!--   # Combine the list of data frames into a single data frame -->
<!--   do.call(bind_rows, bootstrapped_slopes) -->
<!-- } -->

<!-- # Run the bootstrapping in parallel -->
<!-- bootstrapped_slopes_list <- mclapply(1:n_iterations, function(i) { -->
<!--   perform_bootstrap(i, data, n_sample_trees) -->
<!-- }, mc.cores = detectCores() - 1) -->

<!-- # Combine all bootstrap results into a single data frame -->
<!-- bootstrapped_slopes_df <- bind_rows(bootstrapped_slopes_list) -->

<!-- # Calculate CI values -->
<!-- ci_values <- bootstrapped_slopes_df %>% -->
<!--   group_by(round) %>% -->
<!--   drop_na(slope) %>% -->
<!--   mutate(mean_slope_round = mean(slope, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   summarize( -->
<!--     mean = mean(mean_slope_round, na.rm = TRUE), -->
<!--     lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE), -->
<!--     upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE) -->
<!--   ) -->

<!-- # Print the CI values -->
<!-- print(ci_values) -->

<!-- # Calculate overall mean slope and add "pre_post" column -->
<!-- mean_slope_dcwc <- ci_values %>% -->
<!--   mutate(mean_slope = mean(mean, na.rm = TRUE), pre_post = "dcwc leafout") %>% -->
<!--   select(mean_slope, lower_bound, upper_bound, pre_post) %>% -->
<!--   distinct() -->

<!-- print(mean_slope_dcwc) -->

<!-- # Merge unique slope results with the original dataset -->
<!-- dcwc_space <- bootstrapped_slopes_df %>% -->
<!--   select(tree, slope) %>% -->
<!--   distinct() -->

<!-- # Assuming 'data_og_cwc' is defined in your environment -->
<!-- dcwc_df <- merge(dcwc_space, data_og_cwc) -->

<!-- # Print the final merged dataframe -->
<!-- print(dcwc_df) -->

<!-- plotly::ggplotly(dcwc_df %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = week,  -->
<!--                               color = time)) + -->
<!--                    geom_point() +  -->
<!--                    geom_smooth(method = "lm")  -->
<!--                    #facet_wrap(~week, scales = "free") -->
<!--                  ) -->

<!-- dcwc_df %>%  -->
<!--   filter(week > 19) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = water_potential,  -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "Water Potential (MPa)",  -->
<!--        color = "Time") -->

<!-- # Calculate the IQR bounds for the slope column -->
<!-- slope_bounds <- dcwc_df %>% -->
<!--   summarize( -->
<!--     lower_bound = quantile(slope, 0.25) - 1.5 * IQR(slope), -->
<!--     upper_bound = quantile(slope, 0.75) + 1.5 * IQR(slope) -->
<!--   ) -->

<!-- # Filter out rows where slope falls outside of these bounds -->
<!-- dcwc_df_no_outliers <- dcwc_df %>% -->
<!--   filter(slope >= slope_bounds$lower_bound & slope <= slope_bounds$upper_bound) -->

<!-- # Print the cleaned dataset without outliers -->
<!-- print(dcwc_df_no_outliers) -->

<!-- plotly::ggplotly(dcwc_df_no_outliers %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = week,  -->
<!--                               color = time)) + -->
<!--                    geom_point() +  -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    facet_wrap(~week, scales = "free") -->
<!--                  ) -->

<!-- dcwc_df_no_outliers %>%  -->
<!--   #filter(week > 19) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = water_potential,  -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "Water Potential (MPa)",  -->
<!--        color = "Time") -->

<!-- #Are any of the weeks significant? -->

<!-- # Ensure columns are numeric and filter out NAs -->
<!-- filtered_data <- dcwc_df_no_outliers %>% -->
<!--  # filter(week > 19) %>% -->
<!--   mutate( -->
<!--     water_potential = as.numeric(water_potential), -->
<!--     slope = as.numeric(slope) -->
<!--   ) %>% -->
<!--   drop_na(water_potential, slope) # Remove rows with NA in these columns -->

<!-- # Fit a linear model for each date and time combination, then extract p-values and slope estimates -->
<!-- model_results <- filtered_data %>% -->
<!--   group_by(date_wp, time) %>% -->
<!--   group_modify(~ tidy(lm(water_potential ~ slope, data = .x))) %>% -->
<!--   filter(term == "slope") %>% -->
<!--   select(date_wp, time, estimate, std.error, statistic, p.value) -->

<!-- # View the results -->
<!-- print(model_results) -->

<!-- sig_mods_before_mpa <- model_results %>%  -->
<!--   filter(p.value < 0.05)  -->
<!-- sig_mods_before_mpa -->

<!-- dcwc_df_no_outliers %>% -->
<!--   filter((date_wp %in% c(sig_mods_before_mpa$date_wp) & time %in% c(sig_mods_before_mpa$time))) %>% -->
<!--                    ggplot(aes(y = slope, -->
<!--                               x = water_potential, -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() + -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC", -->
<!--        x = "Water Potential (MPa)", -->
<!--        color = "Time") -->

<!-- dcwc_df_no_outliers %>% write_csv(here("processed-data", "dcwc_beforeleafout_df_no_outliers.csv")) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- ##ADD LMA -->

<!-- filtered_data_lma <- merge(data_qudo_lma, filtered_data, by = c("tree", "week"), all = T) %>%  -->
<!--   select(-water_potential.x, -water_potential.y) %>%  -->
<!--   distinct() %>% -->
<!--  # filter(week > 19) %>% -->
<!--   mutate( -->
<!--     lma_g_cm2 = as.numeric(lma_g_cm2), -->
<!--     slope = as.numeric(slope) -->
<!--   ) %>% -->
<!--   drop_na(lma_g_cm2, slope) %>%  -->
<!--   select(tree, week, date_wp, slope, lma_g_cm2) -->

<!-- # Fit a linear model for each date and time combination, then extract p-values and slope estimates -->
<!-- model_results_lma <- filtered_data_lma %>% -->
<!--   group_by(date_wp) %>% -->
<!--   group_modify(~ tidy(lm(lma_g_cm2 ~ slope, data = .x))) %>% -->
<!--   filter(term == "slope") %>% -->
<!--   select(date_wp,  estimate, std.error, statistic, p.value) -->

<!-- # View the results -->
<!-- print(model_results_lma) -->

<!-- model_results_lma %>%  -->
<!--   filter(p.value < 0.1) -->

<!-- # View the results -->
<!-- print(model_results_lma) -->

<!-- sig_mods_before_lma <- model_results_lma %>%  -->
<!--   filter(p.value < 0.05)  -->
<!-- sig_mods_before_lma -->

<!-- filtered_data_lma %>%  -->
<!--   filter((date_wp %in% c(sig_mods_before_lma$date_wp))) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = lma_g_cm2)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "LMA (g/cm2)",  -->
<!--        color = "Time") -->


<!-- ``` -->


<!-- ###Just May (week 18-21) -->
<!-- ```{r} -->
<!-- ###dcwc leafout:  -->
<!-- data <- filtered_data  %>%  -->
<!--   filter(week %in% c(18:21)) %>%  -->
<!--   distinct() %>%  -->
<!--   drop_na(cwc) %>%  -->
<!--   group_by(tree) %>%  -->
<!--   mutate(COUNT = n()) %>%  -->
<!--   filter(!(COUNT == 1)) %>%  -->
<!--   select(-COUNT) -->
<!-- data -->

<!-- unique(data$date_wp) -->

<!-- data %>%  -->
<!--   ggplot(aes(y = cwc, x = date_wp, color = as.factor(tree))) +  -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = F) -->

<!-- #How many unique trees did we sample across these time periods? 39! -->
<!-- num_unique_trees <- length(unique(data$tree)) -->
<!-- cat("Number of unique trees in the dataset:", num_unique_trees, "\n") -->

<!-- #Code to run the bootstrapping in parallel (from ChatGPT): -->

<!-- # Assuming your dataset is called 'data' -->
<!-- # Make sure 'data' is properly loaded dcwc proceeding -->
<!-- # Load necessary libraries -->

<!-- # Define the number of bootstrap iterations -->
<!-- n_iterations <- 1000 -->

<!-- # Number of random trees to sample -->
<!-- n_sample_trees <- 28  # Adjust as needed based on the number of unique trees -->

<!-- # Function to calculate the slope for a specific tree within each iteration -->
<!-- calculate_slope_for_tree <- function(tree_data) { -->
<!--   model <- lm(cwc ~ week, data = tree_data) -->
<!--   return(coef(model)[2])  # Extract the slope coefficient -->
<!-- } -->

<!-- # Function to perform a single bootstrap iteration -->
<!-- perform_bootstrap <- function(i, data, n_sample_trees) { -->
<!--   # Randomly sample 'n_sample_trees' trees with replacement -->
<!--   sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE) -->

<!--   # Calculate slopes for each sampled tree and store the results -->
<!--   bootstrapped_slopes <- lapply(sampled_tree_ids, function(tree_id) { -->
<!--     tree_data <- data %>% filter(tree == tree_id) -->
<!--     slope <- calculate_slope_for_tree(tree_data) -->
<!--     data.frame(tree = tree_id, slope = slope, round = i) -->
<!--   }) -->

<!--   # Combine the list of data frames into a single data frame -->
<!--   do.call(bind_rows, bootstrapped_slopes) -->
<!-- } -->

<!-- # Run the bootstrapping in parallel -->
<!-- bootstrapped_slopes_list <- mclapply(1:n_iterations, function(i) { -->
<!--   perform_bootstrap(i, data, n_sample_trees) -->
<!-- }, mc.cores = detectCores() - 1) -->

<!-- # Combine all bootstrap results into a single data frame -->
<!-- bootstrapped_slopes_df <- bind_rows(bootstrapped_slopes_list) -->

<!-- # Calculate CI values -->
<!-- ci_values <- bootstrapped_slopes_df %>% -->
<!--   group_by(round) %>% -->
<!--   drop_na(slope) %>% -->
<!--   mutate(mean_slope_round = mean(slope, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   summarize( -->
<!--     mean = mean(mean_slope_round, na.rm = TRUE), -->
<!--     lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE), -->
<!--     upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE) -->
<!--   ) -->

<!-- # Print the CI values -->
<!-- print(ci_values) -->

<!-- # Calculate overall mean slope and add "pre_post" column -->
<!-- mean_slope_dcwc <- ci_values %>% -->
<!--   mutate(mean_slope = mean(mean, na.rm = TRUE), pre_post = "dcwc leafout") %>% -->
<!--   select(mean_slope, lower_bound, upper_bound, pre_post) %>% -->
<!--   distinct() -->

<!-- print(mean_slope_dcwc) -->

<!-- # Merge unique slope results with the original dataset -->
<!-- dcwc_space <- bootstrapped_slopes_df %>% -->
<!--   select(tree, slope) %>% -->
<!--   distinct() -->

<!-- # Assuming 'data_og_cwc' is defined in your environment -->
<!-- dcwc_df <- merge(dcwc_space, data_og_cwc) -->

<!-- # Print the final merged dataframe -->
<!-- print(dcwc_df) -->

<!-- plotly::ggplotly(dcwc_df %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = week,  -->
<!--                               color = time)) + -->
<!--                    geom_point() +  -->
<!--                    geom_smooth(method = "lm")  -->
<!--                    #facet_wrap(~week, scales = "free") -->
<!--                  ) -->

<!-- dcwc_df %>%  -->
<!--   filter(week > 19) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = water_potential,  -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "Water Potential (MPa)",  -->
<!--        color = "Time") -->

<!-- # Calculate the IQR bounds for the slope column -->
<!-- slope_bounds <- dcwc_df %>% -->
<!--   summarize( -->
<!--     lower_bound = quantile(slope, 0.25, na.rm = T) - 1.5 * IQR(slope, na.rm = T), -->
<!--     upper_bound = quantile(slope, 0.75, na.rm = T) + 1.5 * IQR(slope, na.rm = T) -->
<!--   ) -->

<!-- # Filter out rows where slope falls outside of these bounds -->
<!-- dcwc_df_no_outliers <- dcwc_df %>% -->
<!--   filter(slope >= slope_bounds$lower_bound & slope <= slope_bounds$upper_bound) -->

<!-- # Print the cleaned dataset without outliers -->
<!-- print(dcwc_df_no_outliers) -->

<!-- plotly::ggplotly(dcwc_df_no_outliers %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = week,  -->
<!--                               color = time)) + -->
<!--                    geom_point() +  -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    facet_wrap(~week, scales = "free") -->
<!--                  ) -->

<!-- dcwc_df_no_outliers %>%  -->
<!--   #filter(week > 19) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = water_potential,  -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "Water Potential (MPa)",  -->
<!--        color = "Time") -->

<!-- #Are any of the weeks significant? -->

<!-- # Ensure columns are numeric and filter out NAs -->
<!-- filtered_data <- dcwc_df_no_outliers %>% -->
<!--  # filter(week > 19) %>% -->
<!--   mutate( -->
<!--     water_potential = as.numeric(water_potential), -->
<!--     slope = as.numeric(slope) -->
<!--   ) %>% -->
<!--   drop_na(water_potential, slope) # Remove rows with NA in these columns -->

<!-- # Fit a linear model for each date and time combination, then extract p-values and slope estimates -->
<!-- model_results <- filtered_data %>% -->
<!--   group_by(date_wp, time) %>% -->
<!--   group_modify(~ tidy(lm(water_potential ~ slope, data = .x))) %>% -->
<!--   filter(term == "slope") %>% -->
<!--   select(date_wp, time, estimate, std.error, statistic, p.value) -->

<!-- # View the results -->
<!-- print(model_results) -->

<!-- sig_mods_may_mpa <- model_results %>%  -->
<!--   filter(p.value < 0.05)  -->
<!--   #filter(p.value < 0.1) -->
<!-- sig_mods_may_mpa -->

<!-- dcwc_df_no_outliers %>% write_csv(here("processed-data", "dcwc_justmay_df_no_outliers.csv")) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- # dcwc_df_no_outliers %>%  -->
<!-- #   filter((date_wp %in% c(sig_mods_may_mpa$date_wp) & time %in% c(sig_mods$time))) %>%  -->
<!-- #                    ggplot(aes(y = slope,  -->
<!-- #                               x = water_potential,  -->
<!-- #                               color = time)) + -->
<!-- #                    geom_smooth(method = "lm") + -->
<!-- #                    geom_point() +  -->
<!-- #                    facet_wrap(~date_wp, scales = "free") + -->
<!-- #   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!-- #   labs(y = "dCWC",  -->
<!-- #        x = "Water Potential (MPa)",  -->
<!-- #        color = "Time") -->

<!-- ##ADD LMA -->

<!-- filtered_data_lma <- merge(data_qudo_lma, filtered_data, by = c("tree", "week"), all = T) %>%  -->
<!--   select(-water_potential.x, -water_potential.y) %>%  -->
<!--   distinct() %>% -->
<!--  # filter(week > 19) %>% -->
<!--   mutate( -->
<!--     lma_g_cm2 = as.numeric(lma_g_cm2), -->
<!--     slope = as.numeric(slope) -->
<!--   ) %>% -->
<!--   drop_na(lma_g_cm2, slope) %>%  -->
<!--   select(tree, week, date_wp, slope, lma_g_cm2) -->

<!-- # Fit a linear model for each date and time combination, then extract p-values and slope estimates -->
<!-- model_results_lma <- filtered_data_lma %>% -->
<!--   group_by(date_wp) %>% -->
<!--   group_modify(~ tidy(lm(lma_g_cm2 ~ slope, data = .x))) %>% -->
<!--   filter(term == "slope") %>% -->
<!--   select(date_wp,  estimate, std.error, statistic, p.value) -->

<!-- # View the results -->
<!-- print(model_results_lma) -->

<!-- model_results_lma %>%  -->
<!--   filter(p.value < 0.1) -->

<!-- # View the results -->
<!-- print(model_results_lma) -->

<!-- sig_mods_may_lma <- model_results_lma %>%  -->
<!--   filter(p.value < 0.05)  -->
<!-- sig_mods_may_lma -->

<!-- filtered_data_lma %>%  -->
<!--   filter((date_wp %in% c(sig_mods_may_lma$date_wp))) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = lma_g_cm2)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "LMA (g/cm2)",  -->
<!--        color = "Time") -->
<!-- ``` -->
<!-- ####Whole date range -->

<!-- ```{r} -->
<!-- ###dcwc leafout:  -->

<!-- data <- filtered_data %>%  -->
<!--   #filter(week %in% c(29:40)) %>%  -->
<!--   distinct() %>%  -->
<!--   drop_na(water_potential, cwc) %>%  -->
<!--   group_by(tree) %>%  -->
<!--   mutate(COUNT = n()) %>%  -->
<!--   filter(!(COUNT == 1)) %>%  -->
<!--   select(-COUNT)  %>% -->
<!--   group_by(tree) %>% -->
<!-- #filter out trees that werent measured in Sept.  -->
<!--   filter( -->
<!--     sum(format(date_wp, "%m") == "05") > 0,  # At least one measurement in May -->
<!--     sum(format(date_wp, "%m") == "09") > 0,  # At least one measurement in September -->
<!--     n() >= 2  # At least two measurements -->
<!--   ) %>% -->
<!--   ungroup() -->
<!-- data -->

<!-- data %>%  -->
<!--   ggplot(aes(y = cwc, x = date_wp, color = as.factor(tree))) +  -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = F) -->


<!-- head(data) -->

<!-- #How many unique trees did we sample across these time periods? 39! -->
<!-- num_unique_trees <- length(unique(data$tree)) -->
<!-- cat("Number of unique trees in the dataset:", num_unique_trees, "\n") -->

<!-- #Code to run the bootstrapping in parallel (from ChatGPT): -->

<!-- # Assuming your dataset is called 'data' -->
<!-- # Make sure 'data' is properly loaded dcwc proceeding -->
<!-- # Load necessary libraries -->

<!-- # Define the number of bootstrap iterations -->
<!-- n_iterations <- 1000 -->

<!-- # Number of random trees to sample -->
<!-- n_sample_trees <- 35  # Adjust as needed based on the number of unique trees -->

<!-- # Function to calculate the slope for a specific tree within each iteration -->
<!-- calculate_slope_for_tree <- function(tree_data) { -->
<!--   model <- lm(cwc ~ week, data = tree_data) -->
<!--   return(coef(model)[2])  # Extract the slope coefficient -->
<!-- } -->

<!-- # Function to perform a single bootstrap iteration -->
<!-- perform_bootstrap <- function(i, data, n_sample_trees) { -->
<!--   # Randomly sample 'n_sample_trees' trees with replacement -->
<!--   sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE) -->

<!--   # Calculate slopes for each sampled tree and store the results -->
<!--   bootstrapped_slopes <- lapply(sampled_tree_ids, function(tree_id) { -->
<!--     tree_data <- data %>% filter(tree == tree_id) -->
<!--     slope <- calculate_slope_for_tree(tree_data) -->
<!--     data.frame(tree = tree_id, slope = slope, round = i) -->
<!--   }) -->

<!--   # Combine the list of data frames into a single data frame -->
<!--   do.call(bind_rows, bootstrapped_slopes) -->
<!-- } -->

<!-- # Run the bootstrapping in parallel -->
<!-- bootstrapped_slopes_list <- mclapply(1:n_iterations, function(i) { -->
<!--   perform_bootstrap(i, data, n_sample_trees) -->
<!-- }, mc.cores = detectCores() - 1) -->

<!-- # Combine all bootstrap results into a single data frame -->
<!-- bootstrapped_slopes_df <- bind_rows(bootstrapped_slopes_list) -->

<!-- # Calculate CI values -->
<!-- ci_values <- bootstrapped_slopes_df %>% -->
<!--   group_by(round) %>% -->
<!--   drop_na(slope) %>% -->
<!--   mutate(mean_slope_round = mean(slope, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   summarize( -->
<!--     mean = mean(mean_slope_round, na.rm = TRUE), -->
<!--     lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE), -->
<!--     upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE) -->
<!--   ) -->

<!-- # Print the CI values -->
<!-- print(ci_values) -->

<!-- # Calculate overall mean slope and add "pre_post" column -->
<!-- mean_slope_dcwc <- ci_values %>% -->
<!--   mutate(mean_slope = mean(mean, na.rm = TRUE), pre_post = "dcwc leafout") %>% -->
<!--   select(mean_slope, lower_bound, upper_bound, pre_post) %>% -->
<!--   distinct() -->

<!-- print(mean_slope_dcwc) -->

<!-- # Merge unique slope results with the original dataset -->
<!-- dcwc_space <- bootstrapped_slopes_df %>% -->
<!--   select(tree, slope) %>% -->
<!--   distinct() -->

<!-- # Assuming 'data_og_cwc' is defined in your environment -->
<!-- dcwc_df <- merge(dcwc_space, data_og_cwc) -->

<!-- # Print the final merged dataframe -->
<!-- print(dcwc_df) -->

<!-- plotly::ggplotly(dcwc_df %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = week,  -->
<!--                               color = time)) + -->
<!--                    geom_point() +  -->
<!--                    geom_smooth(method = "lm")  -->
<!--                    #facet_wrap(~week, scales = "free") -->
<!--                  ) -->

<!-- dcwc_df %>%  -->
<!--   filter(week > 19) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = water_potential,  -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "Water Potential (MPa)",  -->
<!--        color = "Time") -->

<!-- # Calculate the IQR bounds for the slope column -->
<!-- slope_bounds <- dcwc_df %>% -->
<!--   summarize( -->
<!--     lower_bound = quantile(slope, 0.25) - 1.5 * IQR(slope), -->
<!--     upper_bound = quantile(slope, 0.75) + 1.5 * IQR(slope) -->
<!--   ) -->

<!-- # Filter out rows where slope falls outside of these bounds -->
<!-- dcwc_df_no_outliers <- dcwc_df %>% -->
<!--   filter(slope >= slope_bounds$lower_bound & slope <= slope_bounds$upper_bound) -->

<!-- # Print the cleaned dataset without outliers -->
<!-- print(dcwc_df_no_outliers) -->

<!-- plotly::ggplotly(dcwc_df_no_outliers %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = week,  -->
<!--                               color = time)) + -->
<!--                    geom_point() +  -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    facet_wrap(~week, scales = "free") -->
<!--                  ) -->

<!-- dcwc_df_no_outliers %>%  -->
<!--   #filter(week > 19) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = water_potential,  -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "Water Potential (MPa)",  -->
<!--        color = "Time") -->

<!-- #Are any of the weeks significant? -->

<!-- # Ensure columns are numeric and filter out NAs -->
<!-- filtered_data <- dcwc_df_no_outliers %>% -->
<!--  # filter(week > 19) %>% -->
<!--   mutate( -->
<!--     water_potential = as.numeric(water_potential), -->
<!--     slope = as.numeric(slope) -->
<!--   ) %>% -->
<!--   drop_na(water_potential, slope) # Remove rows with NA in these columns -->

<!-- # Fit a linear model for each date and time combination, then extract p-values and slope estimates -->
<!-- model_results <- filtered_data %>% -->
<!--   group_by(date_wp, time) %>% -->
<!--   group_modify(~ tidy(lm(water_potential ~ slope, data = .x))) %>% -->
<!--   filter(term == "slope") %>% -->
<!--   select(date_wp, time, estimate, std.error, statistic, p.value) -->

<!-- # View the results -->
<!-- print(model_results) -->

<!-- sig_mods_all_mpa <- model_results %>%  -->
<!--   filter(p.value < 0.05)  -->
<!--   #filter(p.value < 0.1) -->
<!-- sig_mods_all_mpa -->

<!-- dcwc_df_no_outliers %>% -->
<!--   filter((date_wp %in% c(sig_mods_all_mpa$date_wp) & time %in% c(sig_mods_all_mpa$time))) %>% -->
<!--                    ggplot(aes(y = slope, -->
<!--                               x = water_potential, -->
<!--                               color = time)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() + -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC", -->
<!--        x = "Water Potential (MPa)", -->
<!--        color = "Time") -->
<!-- ##ADD LMA -->

<!-- filtered_data_lma <- merge(data_qudo_lma, filtered_data, by = c("tree", "week"), all = T) %>%  -->
<!--   select(-water_potential.x, -water_potential.y) %>%  -->
<!--   distinct() %>% -->
<!--  # filter(week > 19) %>% -->
<!--   mutate( -->
<!--     lma_g_cm2 = as.numeric(lma_g_cm2), -->
<!--     slope = as.numeric(slope) -->
<!--   ) %>% -->
<!--   drop_na(lma_g_cm2, slope) %>%  -->
<!--   select(tree, week, date_wp, slope, lma_g_cm2) -->

<!-- # Fit a linear model for each date and time combination, then extract p-values and slope estimates -->
<!-- model_results_lma <- filtered_data_lma %>% -->
<!--   group_by(date_wp) %>% -->
<!--   group_modify(~ tidy(lm(lma_g_cm2 ~ slope, data = .x))) %>% -->
<!--   filter(term == "slope") %>% -->
<!--   select(date_wp,  estimate, std.error, statistic, p.value) -->

<!-- # View the results -->
<!-- print(model_results_lma) -->

<!-- model_results_lma %>%  -->
<!--   filter(p.value < 0.1) -->

<!-- # View the results -->
<!-- print(model_results_lma) -->

<!-- sig_mods_all_lma <- model_results_lma %>%  -->
<!--   filter(p.value < 0.05)  -->
<!-- sig_mods_all_lma -->

<!-- filtered_data_lma %>%  -->
<!--   #filter((date_wp %in% c(sig_mods_all_lma$date_wp))) %>%  -->
<!--   filter((date_wp %in% c("2022-03-08",  -->
<!--                          "2022-05-23") -->
<!--           )) %>%  -->
<!--                    ggplot(aes(y = slope,  -->
<!--                               x = lma_g_cm2)) + -->
<!--                    geom_smooth(method = "lm") + -->
<!--                    geom_point() +  -->
<!--                    facet_wrap(~date_wp, scales = "free") + -->
<!--   scale_color_manual(values = c("#C969A1","#165E6F")) + -->
<!--   labs(y = "dCWC",  -->
<!--        x = "LMA (g/cm2)",  -->
<!--        color = "Time") -->

<!-- dcwc_df_no_outliers %>% write_csv(here("processed-data", "dcwc_wholedaterange_df_no_outliers.csv")) -->
<!-- ``` -->
<!-- #TABLE:  -->

<!-- ```{r} -->
<!-- sig_mods_all_mpa_lma <- bind_rows(sig_mods_all_mpa %>% mutate(var = "mpa", -->
<!--                                                       timeframe = "whole timeframe"),  -->
<!--                           sig_mods_whole_mpa %>% mutate(var = "mpa", -->
<!--                                                       timeframe = "after leaf expansion"),  -->
<!--                           sig_mods_before_mpa%>% mutate(var = "mpa", -->
<!--                                                       timeframe = "before leaf expansion"),  -->
<!--                           sig_mods_may_mpa%>% mutate(var = "mpa", -->
<!--                                                       timeframe = "just May"), -->
<!--                           sig_mods_all_lma%>% mutate(var = "LMA", -->
<!--                                                       timeframe = "whole timeframe"), -->
<!--                           sig_mods_whole_lma%>% mutate(var = "LMA", -->
<!--                                                       timeframe = "after leaf expansion"), -->
<!--                           sig_mods_before_lma%>% mutate(var = "LMA", -->
<!--                                                       timeframe = "before leaf expansion"),  -->
<!--                           sig_mods_may_lma%>% mutate(var = "LMA", -->
<!--                                                       timeframe = "just May"), -->
<!--                           ) %>%  -->
<!--   select(var, timeframe,date_wp, time, estimate, p.value) -->

<!-- sig_mods_all_mpa_lma -->

<!-- write_csv(sig_mods_all_mpa_lma, here("processed-data", "model results", "dcwc_mods.csv")) -->
<!-- ``` -->

<!-- #----------------- -->



