---
title: "6.0_models_r2r"
author: "Indra Boving"
date: "2025-02-14"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(rstatix)
library(vars)
library(MuMIn)
library(lme4) #for mixed effects models
library(arm)
library(nlme)
select = dplyr::select
library(broom.mixed)  # For tidy output of mixed models
library(readr)

#source(here::here("scripts", "scripts_functions", "figure_info.R"))

datver <- "20230724" #make sure this matches the datver in the processing script
dataversion <- paste0("Data_", datver)
```

Need: MPa, LAI, LMA, LWA data

# DATA:

```{r}
data_og_cwc <- read_csv(here("processed-data", paste0("cwc_analysis",datver,".csv")), show_col_types = F) %>%  
  filter(species %in% c("blue oak")) %>% 
  select(tree, week, water_potential, cwc, time_season, time, site, date_wp, date_shift) %>% 
  mutate(water_potential = -1*water_potential) %>% 
  distinct() %>% 
   # filter(!tree %in% c(2012, 2011)) %>% 
  filter(!(tree %in% c(2346))) %>% #this tree seems to have a problem with post-leafout cwc - all 0s - likely becuase the canopy was too small to see. 
  filter(!week %in% c(11, 9, 18)) #week 11 only has 9 midday measurements and acts really odd (2022-03-15), 9 just had 3 measurements 

##LMA, LWA, LWC data: 
data_qudo_lma <- read_csv(here("data", paste0("wp_wc_rwc_",datver,".csv"))) %>% 
 # filter(time %in% c("md")) %>% 
  group_by(tree, week) %>% 
  mutate(lwa_g_cm2 = lwa_g_cm2_new, #use the 'new' version, increases sample size because this includes estimates from bulk data.
         lma_g_cm2 = mean(lma_g_cm2_new, na.rm = T), 
         water_potential = -1*water_potential) %>% 
  filter(species %in% c("blue oak")) %>% 
  select(week, time, tree, species, lma_g_cm2, water_potential, lwc_mean, lwa_g_cm2) %>% 
  distinct()

df0 <- merge(data_qudo_lma, data_og_cwc %>% select(-water_potential),
            , by = c("tree", "week", "time"), all = T) %>% 
  mutate(season = case_when(
    week %in% c(1:29) ~ "spring/early summer",
    week %in% c(30:45) ~ "late summer/fall"
  )) 

##LAI data: 

data_qudo_lai_spring <-  read_csv(here("data", "LAI_final.csv")) %>% 
  clean_names() %>% 
  select(treestr, springlai) %>% 
  mutate(tree = as.numeric(treestr))

lai_raw <-  read_csv(here("data", "LAI_final.csv")) %>% 
  clean_names() %>% 
  select(-difflai, -species, -springstdev)

data_qudo_lai_df <-  lai_raw %>% 
  pivot_longer(names_to = "time",
               values_to = "lai",
               cols = c(2:5)) %>% 
  mutate(tree = as.numeric(treestr)) %>% 
  mutate(season = case_when(
    time %in% c("springlai") ~ "spring/early summer",
    time %in% c("septlai") ~ "late summer/fall"
  )) %>% 
  drop_na(season) %>% 
  select(-time)
         
df <- merge(df0, data_qudo_lai_df, 
            by = c("tree", "season"),
            all.x = T)

df_nodates <- df %>% 
  filter(is.na(date_wp))
```

Data explanation:

-   LMa and LWa are measured concurrent with WP (and CWC when those
    occured)

-   LAI is from 2 measurements: spring and september. Spring LAI is
    associated with CWC and in-situ data from start of campaign (March)
    though July, September LAI is associated with sampling dates in
    August and September.

```{r}
df %>% 
  filter(time == "md") %>% 
  ggplot(aes(y = lai, 
             x = lma_g_cm2, 
             #color = time_season, 
             color = as.factor(date_wp))) +
  geom_point()+
  geom_smooth(method = "lm", se = F)

df %>% 
   filter(time == "md") %>% 
  ggplot(aes(y = lai, 
             x = lwa_g_cm2, 
             color = as.factor(date_wp))) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

df %>% 
   filter(time == "md") %>% 
  ggplot(aes(y = lai, 
             x = cwc, 
             color = as.factor(date_wp))) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

df %>% 
   filter(time == "md",
          cwc > 0) %>% 
  ggplot(aes(x = lai, 
             y = cwc, 
             color = as.factor(date_wp))) +
  geom_point() +
  geom_smooth(method = "lm", se = F)
```


```{r}
df %>% 
   filter(time == "md") %>% 
  ggplot(aes(y = lai, 
             x = water_potential, 
             color = as.factor(week))) +
  geom_point() +
  facet_wrap(~time) +
  geom_smooth(method = "lm", se = F)

df %>% 
   filter(time == "md") %>% 
  ggplot(aes(x = lwc_mean, 
             y = lai, 
             color = as.factor(week))) +
  geom_point() +
  facet_wrap(~time) +
  geom_smooth(method = "lm", se = F)

df %>% 
   filter(time == "pd") %>% 
  ggplot(aes(y = lai, 
             x = water_potential, 
             #size = as.factor(week),
             color = as.factor(tree))) +
  geom_point() +
  facet_wrap(~time) +
  geom_smooth(method = "lm", se = F)

df %>% 
   filter(time == "md") %>% 
  ggplot(aes(x = lwa_g_cm2, 
             y = cwc, 
             #size = as.factor(week),
             color = as.factor(week))) +
  geom_point() +
  facet_wrap(~time) +
  geom_smooth(method = "lm", se = F)
```

```{r}
df_lai <- df %>% 
  mutate(cwc_ground = lma_g_cm2*lwc_mean*lai)

df_lai %>% 
  # filter(time == "md") %>% 
  ggplot(aes(y = cwc, 
             x = cwc_ground, 
             #size = as.factor(week),
             color = as.factor(week))) +
  geom_point() +
  facet_wrap(~time) +
  geom_smooth(method = "lm", se = F)

df_lai %>% 
   filter(cwc > 0) %>% 
  ggplot(aes(y = cwc, 
             x = cwc_ground, 
             #size = as.factor(week),
             color = as.factor(week))) +
  geom_point() +
  facet_wrap(~time) +
  geom_smooth(method = "lm", se = F)

length(which(is.na(df_lai$lwa_g_cm2)))
```

# CWC models:

These do not account for spatial vs. temporal analysis with random
effects, instead this is looking at relationships across the whole
dataset:

```{r}
# Filter the data to exclude rows with missing values in the variables of interest
df_filtered <- df %>% 
  mutate(cwc_ground = lma_g_cm2*lwc_mean*lai) %>% 
  filter(time %in% c("md"), 
         cwc > 0) %>% #removing all of the 0 CWCs REALLY reduces the sample size (>200 down to <100), but seems like we should given that it doesn't tell us much except that the trees are probably dry?
  filter(!is.na(cwc) & !is.na(lma_g_cm2) & !is.na(water_potential & !is.na(lwc_mean)) & !is.na(lai))

# Fit models suggested by reviewer 3:
model_lwa_lai <- lmer(cwc ~ lwa_g_cm2 * lai + (1 | tree), data = df_filtered)
model_lwc_lma_lai <- lmer(cwc ~ lwc_mean * lma_g_cm2 * lai + (1 | tree), data = df_filtered)
model_ground <- lmer(cwc ~ cwc_ground + (1 | tree), data = df_filtered)

# Additional models
model_lai <- lmer(cwc ~ lai + (1 | tree), data = df_filtered) #does LAI along predict CWC? 
model_cwc <- lmer(cwc ~ water_potential + (1 | tree), data = df_filtered) #does midday MPa predict CWC?
model_lma <- lmer(cwc ~ lma_g_cm2 + (1 | tree), data = df_filtered) #Does LMA?
model_time_season <- lmer(cwc ~ time_season + (1 | tree), data = df_filtered) #Does just being before vs. after leafout?
model_lwa <- lmer(cwc ~ lwa_g_cm2 + (1 | tree), data = df_filtered) #Does LWA? This is the ground level analogue to CWC, so it probably should if CWC actually captures leaf water... 
model_lwc <- lmer(cwc ~ lwc_mean + (1 | tree), data = df_filtered) #Does LWC?
```
```{r}
library(car)
qqp(resid(model_cwc))
```


```{r}
# List of models
models <- list(
  lwa_lai = model_lwa_lai,
  lwc_lma_lai = model_lwc_lma_lai,
  lai = model_lai,
  cwc = model_cwc,
  lma = model_lma,
  time_season = model_time_season,
  lwa = model_lwa,
  lwc = model_lwc,
  cwc_ground = model_ground
)

# Create a summary table of AIC for each model
model_summary <- bind_rows(
  lapply(names(models), function(model_name) {
    model <- models[[model_name]]
    model_aic <- AIC(model)
    model_coeffs <- tidy(model) %>% select(term, estimate) %>% pivot_wider(names_from = term, values_from = estimate)
    
    # Collect model structure (excluding random effect part)
    model_formula <- deparse(formula(model))
    model_formula <- gsub("\\s*\\+\\s*\\(1\\s*\\|\\s*tree\\)", "", model_formula)  # Remove random effect part
    
    model_data <- data.frame(
      model = model_formula,
      AIC = model_aic,
      delta_AIC = model_aic - min(sapply(models, AIC))
    )
    
    bind_cols(model_data, model_coeffs)
  })
)

# Get models within 10 AIC points of the top model
min_aic <- min(model_summary$AIC)
top_models <- model_summary %>% filter(AIC <= min_aic + 10) %>% 
  arrange(delta_AIC)

# Save final table
#write_csv(top_models, here("processed-data", "model results", "qudo_top_models_cwc.csv"))

# Print the table
print(top_models)
```

```{r}
#attempt to view: 
ggplot(df_filtered, aes(y = cwc, 
                x = lwc_mean, 
                color = week)) +
  geom_point()

ggplot(df_filtered, aes(y = cwc, 
                x = lma_g_cm2, 
                color = week)) +
  geom_point()

ggplot(df_filtered, aes(y = cwc, 
                x = lai, 
                color = week)) +
  geom_point()
```


Models the reviewer wanted us to look at:

```{r}
# Save separate table for specific models
selected_models <- model_summary %>% filter(model %in% c("cwc ~ lwa_g_cm2 * lai", "cwc ~ lwc_mean * lma_g_cm2 * lai", "cwc ~ lai")) %>% 
  arrange(delta_AIC)
write_csv(selected_models, here("processed-data", "model results", "qudo_selected_models_cwc.csv"))

# Print the selected models table
print(selected_models)
```

Best model by AIC: *cwc \~ lwc_mean \* lma_g_cm2 \* lai*

```{r}
print(model_lwc_lma_lai)

# Model assumption checks for a single model
par(mfrow = c(2, 2))  # Set up a 2x2 plotting area

# Residuals vs. Fitted plot
plot(model_lwc_lma_lai, which = 1, main = "Residuals vs Fitted - LWA & LAI Model")

# QQ Plot of residuals
qqnorm(residuals(model_lwc_lma_lai), main = "QQ Plot - LWA & LAI Model")
qqline(residuals(model_lwc_lma_lai))

# Histogram of residuals
hist(residuals(model_lwc_lma_lai), main = "Histogram of Residuals - LWA & LAI Model", xlab = "Residuals")

# Fitted values vs. Residuals
plot(fitted(model_lwc_lma_lai), residuals(model_lwc_lma_lai), 
     main = "Fitted vs Residuals - LWA & LAI Model", 
     xlab = "Fitted values", ylab = "Residuals")

```

# MPa models, just MIDDAYS:

```{r}
# Filter the data to exclude rows with missing values in the variables of interest
df_filtered <- df %>% 
  filter(time %in% c("md"), 
        # cwc > 0 #removing all of the 0 CWCs REALLY reduces the sample size, and also doesnt make a difference for the top mod. 
         ) %>% 
  filter(!is.na(cwc) & !is.na(lma_g_cm2) & !is.na(water_potential) & !is.na(lai))

# Fit models with different combinations of predictors
model_cwc <- lmer(water_potential ~ cwc + (1 | tree), data = df_filtered)
model_cwc_time <- lmer(water_potential ~ cwc*time_season + (1 | tree), data = df_filtered)
model_lma <- lmer(water_potential ~ lma_g_cm2 + (1 | tree), data = df_filtered)
model_lwa <- lmer(water_potential ~ lwa_g_cm2 + (1 | tree), data = df_filtered)
model_lwc <- lmer(water_potential ~ lwc_mean + (1 | tree), data = df_filtered)
model_lai <- lmer(water_potential ~ lai + (1 | tree), data = df_filtered)
model_lwa_lai <- lmer(water_potential ~ lai*lwa_g_cm2 + (1 | tree), data = df_filtered)
model_lwc_lma_lai <- lmer(water_potential ~ lai*lwc_mean*lma_g_cm2 + (1 | tree), data = df_filtered)


# List of models
models <- list(
  cwc = model_cwc,
  lma = model_lma,
  lwa = model_lwa,
  lwc = model_lwc,
  lai = model_lai,
  cwc_time = model_cwc_time,
  lwa_lai = model_lwa_lai,
  lwc_lma_lai = model_lwc_lma_lai
)


# Create a summary table of AIC for each model
model_summary <- bind_rows(
  lapply(names(models), function(model_name) {
    model <- models[[model_name]]
    model_aic <- AIC(model)
    model_coeffs <- tidy(model) %>% select(term, estimate) %>% pivot_wider(names_from = term, values_from = estimate)
    
    # Collect model structure (excluding random effect part)
    model_formula <- deparse(formula(model))
    model_formula <- gsub("\\s*\\+\\s*\\(1\\s*\\|\\s*tree\\)", "", model_formula)  # Remove random effect part
    
    model_data <- data.frame(
      model = model_formula,
      AIC = model_aic,
      delta_AIC = model_aic - min(sapply(models, AIC))
    )
    
    bind_cols(model_data, model_coeffs)
  })
)

# Get top 5 models by AIC
model_summary <- model_summary %>% arrange(AIC) 
# Get models within 10 AIC points of the top model
min_aic <- min(model_summary$AIC)

top_models <- model_summary %>% filter(AIC <= min_aic + 50) %>% 
  arrange(delta_AIC)


# Save final table
#write_csv(top_models, here("processed-data", "model results", "qudo_top5_mems_mpa_middays.csv"))

# Print the table
print(top_models)
```

Best model by AIC: *water_potential \~ lai \* lwc_mean \* lma_g_cm2*

```{r}
print(model_lwc_lma_lai)

#attempt to view: 
ggplot(df_filtered, aes(y = water_potential, 
                x = lwc_mean,
                color = lma_g_cm2, 
                size = lai)) +
  geom_point()

# Model assumption checks for a single model
par(mfrow = c(2, 2))  # Set up a 2x2 plotting area

# Residuals vs. Fitted plot
plot(model_lwc_lma_lai, which = 1, main = "Residuals vs Fitted - LWC*LAI*LMA Model")

# QQ Plot of residuals
qqnorm(residuals(model_lwc_lma_lai), main = "QQ Plot - LWC*LAI*LMA Model")
qqline(residuals(model_lwc_lma_lai))

# Histogram of residuals
hist(residuals(model_lwc_lma_lai), main = "Histogram of Residuals - LWC*LAI*LMA Model", xlab = "Residuals")

# Fitted values vs. Residuals
plot(fitted(model_lwc_lma_lai), residuals(model_lwc_lma_lai), 
     main = "Fitted vs Residuals - LWC*LAI*LMA Model", 
     xlab = "Fitted values", ylab = "Residuals")

```

# MPa models, just PREDAWN:

```{r}
# Filter the data to exclude rows with missing values in the variables of interest
df_filtered <- df %>% 
  filter(time %in% c("pd"), 
        # cwc > 0 #removing all of the 0 CWCs REALLY reduces the sample size, and also doesnt make a difference for the top mod. 
         ) %>% 
  filter(!is.na(cwc) & !is.na(lma_g_cm2) & !is.na(water_potential) & !is.na(lai))

# Fit models with different combinations of predictors
model_cwc <- lmer(water_potential ~ cwc + (1 | tree), data = df_filtered)
model_cwc_time <- lmer(water_potential ~ cwc*time_season + (1 | tree), data = df_filtered)
model_lma <- lmer(water_potential ~ lma_g_cm2 + (1 | tree), data = df_filtered)
model_lwa <- lmer(water_potential ~ lwa_g_cm2 + (1 | tree), data = df_filtered)
model_lwc <- lmer(water_potential ~ lwc_mean + (1 | tree), data = df_filtered)
model_lai <- lmer(water_potential ~ lai + (1 | tree), data = df_filtered)
model_lwa_lai <- lmer(water_potential ~ lai*lwa_g_cm2 + (1 | tree), data = df_filtered)
model_lwc_lma_lai <- lmer(water_potential ~ lai*lwc_mean*lma_g_cm2 + (1 | tree), data = df_filtered)


# List of models
models <- list(
  cwc = model_cwc,
  lma = model_lma,
  lwa = model_lwa,
  lwc = model_lwc,
  lai = model_lai,
  cwc_time = model_cwc_time,
  lwa_lai = model_lwa_lai,
  lwc_lma_lai = model_lwc_lma_lai
)


# Create a summary table of AIC for each model
model_summary <- bind_rows(
  lapply(names(models), function(model_name) {
    model <- models[[model_name]]
    model_aic <- AIC(model)
    model_coeffs <- tidy(model) %>% select(term, estimate) %>% pivot_wider(names_from = term, values_from = estimate)
    
    # Collect model structure (excluding random effect part)
    model_formula <- deparse(formula(model))
    model_formula <- gsub("\\s*\\+\\s*\\(1\\s*\\|\\s*tree\\)", "", model_formula)  # Remove random effect part
    
    model_data <- data.frame(
      model = model_formula,
      AIC = model_aic,
      delta_AIC = model_aic - min(sapply(models, AIC))
    )
    
    bind_cols(model_data, model_coeffs)
  })
)

# Get top 5 models by AIC
model_summary <- model_summary %>% arrange(AIC) 
# Get models within 10 AIC points of the top model
min_aic <- min(model_summary$AIC)

top_models <- model_summary %>% filter(AIC <= min_aic + 50) %>% 
  arrange(delta_AIC)


# Save final table
#write_csv(top_models, here("processed-data", "model results", "qudo_top5_mems_mpa_middays.csv"))

# Print the table
print(top_models)
```

Best model by AIC: *water_potential \~ lai \* lwc_mean \* lma_g_cm2*

```{r}
print(model_cwc_time)

#attempt to view: 
ggplot(df_filtered, aes(y = water_potential, 
                x = cwc,
                color = time_season)) +
  geom_point()

# Model assumption checks for a single model
par(mfrow = c(2, 2))  # Set up a 2x2 plotting area

# Residuals vs. Fitted plot
plot(model_cwc_time, which = 1, main = "Residuals vs Fitted - CWC + time_season Model")

# QQ Plot of residuals
qqnorm(residuals(model_cwc_time), main = "QQ Plot - CWC + time_season Model")
qqline(residuals(model_cwc_time))

# Histogram of residuals
hist(residuals(model_cwc_time), main = "Histogram of Residuals - CWC + time_season Model", xlab = "Residuals")

# Fitted values vs. Residuals
plot(fitted(model_cwc_time), residuals(model_cwc_time), 
     main = "Fitted vs Residuals - CWC + time_season Model", 
     xlab = "Fitted values", ylab = "Residuals")

```

But, there are so many CWC = 0 here, what happens if we remove them:

### MPa models, just PREDAWN, filtered CWC

```{r}
# Filter the data to exclude rows with missing values in the variables of interest
df_filtered <- df %>% 
  filter(time %in% c("pd"), 
         cwc > 0 
         ) %>% 
  filter(!is.na(cwc) & !is.na(lma_g_cm2) & !is.na(water_potential) & !is.na(lai))

# Fit models with different combinations of predictors
model_cwc <- lmer(water_potential ~ cwc + (1 | tree), data = df_filtered)
model_cwc_time <- lmer(water_potential ~ cwc*time_season + (1 | tree), data = df_filtered)
model_lma <- lmer(water_potential ~ lma_g_cm2 + (1 | tree), data = df_filtered)
model_lwa <- lmer(water_potential ~ lwa_g_cm2 + (1 | tree), data = df_filtered)
model_lwc <- lmer(water_potential ~ lwc_mean + (1 | tree), data = df_filtered)
model_lai <- lmer(water_potential ~ lai + (1 | tree), data = df_filtered)
model_lwa_lai <- lmer(water_potential ~ lai*lwa_g_cm2 + (1 | tree), data = df_filtered)
model_lwc_lma_lai <- lmer(water_potential ~ lai*lwc_mean*lma_g_cm2 + (1 | tree), data = df_filtered)


# List of models
models <- list(
  cwc = model_cwc,
  lma = model_lma,
  lwa = model_lwa,
  lwc = model_lwc,
  lai = model_lai,
  cwc_time = model_cwc_time,
  lwa_lai = model_lwa_lai,
  lwc_lma_lai = model_lwc_lma_lai
)


# Create a summary table of AIC for each model
model_summary <- bind_rows(
  lapply(names(models), function(model_name) {
    model <- models[[model_name]]
    model_aic <- AIC(model)
    model_coeffs <- tidy(model) %>% select(term, estimate) %>% pivot_wider(names_from = term, values_from = estimate)
    
    # Collect model structure (excluding random effect part)
    model_formula <- deparse(formula(model))
    model_formula <- gsub("\\s*\\+\\s*\\(1\\s*\\|\\s*tree\\)", "", model_formula)  # Remove random effect part
    
    model_data <- data.frame(
      model = model_formula,
      AIC = model_aic,
      delta_AIC = model_aic - min(sapply(models, AIC))
    )
    
    bind_cols(model_data, model_coeffs)
  })
)

# Get top 5 models by AIC
model_summary <- model_summary %>% arrange(AIC) 
# Get models within 10 AIC points of the top model
min_aic <- min(model_summary$AIC)

top_models <- model_summary %>% filter(AIC <= min_aic + 50) %>% 
  arrange(delta_AIC)


# Save final table
#write_csv(top_models, here("processed-data", "model results", "qudo_top5_mems_mpa_middays.csv"))

# Print the table
print(top_models)
```

Same thing! CWC time is still the top model:

```{r}
print(model_cwc_time)

#attempt to view: 
ggplot(df_filtered, aes(y = water_potential, 
                x = cwc,
                color = time_season)) +
  geom_point()

# Model assumption checks for a single model
par(mfrow = c(2, 2))  # Set up a 2x2 plotting area

# Residuals vs. Fitted plot
plot(model_cwc_time, which = 1, main = "Residuals vs Fitted - CWC + time_season Model")

# QQ Plot of residuals
qqnorm(residuals(model_cwc_time), main = "QQ Plot - CWC + time_season Model")
qqline(residuals(model_cwc_time))

# Histogram of residuals
hist(residuals(model_cwc_time), main = "Histogram of Residuals - CWC + time_season Model", xlab = "Residuals")

# Fitted values vs. Residuals
plot(fitted(model_cwc_time), residuals(model_cwc_time), 
     main = "Fitted vs Residuals - CWC + time_season Model", 
     xlab = "Fitted values", ylab = "Residuals")

```

# SPACE vs. TIME CWC.

```{r}
#TIME: 
model_lwa_lai_time <- lmer(cwc ~ lwa_g_cm2 * lai + (lwa_g_cm2 | tree) + (lai | tree), data = df_filtered) #random slope and intercept for LWA and LAI for each tree over time
model_lwc_lma_lai_time <- lmer(cwc ~ lwc_mean * lma_g_cm2 * lai + (lwa_g_cm2 | tree) + (lai | tree), data = df_filtered) #random slope and intercept for LWC, LMA, and LAI for each tree over time

#SPACE: 
model_lwa_lai_space <- lmer(cwc ~ lwa_g_cm2 * lai + (lwa_g_cm2 | week) + (lai | week), data = df_filtered) #random slope and intercept for LWA and LAI for all trees in a given sample date
model_lwc_lma_lai_space <- lmer(cwc ~ lwc_mean * lma_g_cm2 * lai + (lwa_g_cm2 | week) + (lai | week), data = df_filtered) #random slope and intercept for LWC, LMA, and LAI for all trees in a given sample date

#DIEL not possible with CWC.
```
